
#####################
This file intoduces NA's to a complete dataset of continuous data and outputs as a .csv  
Creates 5 versions of 5%, 10%, 20%, 30% and 40% missing data each
#####################


**Set up the workspace and load libraries**
This approach uses the R package 'imputeR'
imputeR has the *SimIm* function which randomly introduces missing values in a dataset based on a predetermined amount
continuousdata.csv is my dataset that has 12 variables (columns) and 369 rows (individuals) with no missing values

*Variable Names*
FL_L - femur length left
FL_R - femur length right
T1.AP - T1 antero-posterior length
T1.TR - T1 transverse length
L1.AP - L1 antero-posterior length
L1.TR - L1 transverse length

```{r}
rm(list=ls())
library(knitr)
library(imputeR)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2021/imputation")
datmiss<-read.csv("continuousdata.csv", header=T)
```

Assigning the variable names to call later
```{r}
FL_L<-datmiss$FL_Left
FL_R<-datmiss$FL_Right
T1.AP<-datmiss$T1.AP
T1.TR<-datmiss$T1.TR
T5.AP<-datmiss$T5.AP
T5.TR<-datmiss$T5.TR
T10.AP<-datmiss$T10.AP
T10.TR<-datmiss$T10.TR
L1.AP<-datmiss$L1.AP
L1.TR<-datmiss$L1.TR
L3.AP<-datmiss$L3.AP
L3.TR<-datmiss$L3.TR
```

####################
Simulate Missing Data
#####################

The following chunks simulate missing data for each variable separately. As each simulation randomly assigns missing variables, each output will be different. Here we create 5 different versions (FL.L1, FL.L2, etc) of each to get a variety of patterns of missingness to best evaluate imputation methods. 

p=0.05 - sets the percent missing desired. 

Making 5 versions of 5% missing
```{r}
FL.L1.05<-SimIm(FL_L, p=0.05)
FL.L2.05<-SimIm(FL_L, p=0.05)
FL.L3.05<-SimIm(FL_L, p=0.05)
FL.L4.05<-SimIm(FL_L, p=0.05)
FL.L5.05<-SimIm(FL_L, p=0.05)

FL.R1.05<-SimIm(FL_R, p=0.05)
FL.R2.05<-SimIm(FL_R, p=0.05)
FL.R3.05<-SimIm(FL_R, p=0.05)
FL.R4.05<-SimIm(FL_R, p=0.05)
FL.R5.05<-SimIm(FL_R, p=0.05)

T1.AP1.05<-SimIm(T1.AP, p=0.05)
T1.AP2.05<-SimIm(T1.AP, p=0.05)
T1.AP3.05<-SimIm(T1.AP, p=0.05)
T1.AP4.05<-SimIm(T1.AP, p=0.05)
T1.AP5.05<-SimIm(T1.AP, p=0.05)

T1.TR1.05<-SimIm(T1.TR, p=0.05)
T1.TR2.05<-SimIm(T1.TR, p=0.05)
T1.TR3.05<-SimIm(T1.TR, p=0.05)
T1.TR4.05<-SimIm(T1.TR, p=0.05)
T1.TR5.05<-SimIm(T1.TR, p=0.05)

T5.AP1.05<-SimIm(T5.AP, p=0.05)
T5.AP2.05-SimIm(T5.AP, p=0.05)
T5.AP3.05<-SimIm(T5.AP, p=0.05)
T5.AP4.05<-SimIm(T5.AP, p=0.05)
T5.AP5.05<-SimIm(T5.AP, p=0.05)

T5.TR1.05<-SimIm(T5.TR, p=0.05)
T5.TR2.05<-SimIm(T5.TR, p=0.05)
T5.TR3.05<-SimIm(T5.TR, p=0.05)
T5.TR4.05<-SimIm(T5.TR, p=0.05)
T5.TR5.05<-SimIm(T5.TR, p=0.05)

T10.AP1.05<-SimIm(T10.AP, p=0.05)
T10.AP2.05<-SimIm(T10.AP, p=0.05)
T10.AP3.05<-SimIm(T10.AP, p=0.05)
T10.AP4.05<-SimIm(T10.AP, p=0.05)
T10.AP5.05<-SimIm(T10.AP, p=0.05)

T10.TR1.05<-SimIm(T10.TR, p=0.05)
T10.TR2.05<-SimIm(T10.TR, p=0.05)
T10.TR3.05<-SimIm(T10.TR, p=0.05)
T10.TR4.05<-SimIm(T10.TR, p=0.05)
T10.TR5.05<-SimIm(T10.TR, p=0.05)

L1.AP1.05<-SimIm(L1.AP, p=0.05)
L1.AP2.05<-SimIm(L1.AP, p=0.05)
L1.AP3.05<-SimIm(L1.AP, p=0.05)
L1.AP4.05<-SimIm(L1.AP, p=0.05)
L1.AP5.05<-SimIm(L1.AP, p=0.05)

L1.TR1.05<-SimIm(L1.TR, p=0.05)
L1.TR2.05<-SimIm(L1.TR, p=0.05)
L1.TR3.05<-SimIm(L1.TR, p=0.05)
L1.TR4.05<-SimIm(L1.TR, p=0.05)
L1.TR5.05<-SimIm(L1.TR, p=0.05)

L3.AP1.05<-SimIm(L3.AP, p=0.05)
L3.AP2.05<-SimIm(L3.AP, p=0.05)
L3.AP3.05<-SimIm(L3.AP, p=0.05)
L3.AP4.05<-SimIm(L3.AP, p=0.05)
L3.AP5.05<-SimIm(L3.AP, p=0.05)

L3.TR1.05<-SimIm(L3.TR, p=0.05)
L3.TR2.05<-SimIm(L3.TR, p=0.05)
L3.TR3.05<-SimIm(L3.TR, p=0.05)
L3.TR4.05<-SimIm(L3.TR, p=0.05)
L3.TR5.05<-SimIm(L3.TR, p=0.05)
```

Making 5 versions of 10% missing data
```{r}
FL.L1.10<-SimIm(FL_L, p=0.10)
FL.L2.10<-SimIm(FL_L, p=0.10)
FL.L3.10<-SimIm(FL_L, p=0.10)
FL.L4.10<-SimIm(FL_L, p=0.10)
FL.L5.10<-SimIm(FL_L, p=0.10)

FL.R1.10<-SimIm(FL_R, p=0.10)
FL.R2.10<-SimIm(FL_R, p=0.10)
FL.R3.10<-SimIm(FL_R, p=0.10)
FL.R4.10<-SimIm(FL_R, p=0.10)
FL.R5.10<-SimIm(FL_R, p=0.10)

T1.AP1.10<-SimIm(T1.AP, p=0.10)
T1.AP2.10<-SimIm(T1.AP, p=0.10)
T1.AP3.10<-SimIm(T1.AP, p=0.10)
T1.AP4.10<-SimIm(T1.AP, p=0.10)
T1.AP5.10<-SimIm(T1.AP, p=0.10)

T1.TR1.10<-SimIm(T1.TR, p=0.10)
T1.TR2.10<-SimIm(T1.TR, p=0.10)
T1.TR3.10<-SimIm(T1.TR, p=0.10)
T1.TR4.10<-SimIm(T1.TR, p=0.10)
T1.TR5.10<-SimIm(T1.TR, p=0.10)

T5.AP1.10<-SimIm(T5.AP, p=0.10)
T5.AP2.10<-SimIm(T5.AP, p=0.10)
T5.AP3.10<-SimIm(T5.AP, p=0.10)
T5.AP4.10<-SimIm(T5.AP, p=0.10)
T5.AP5.10<-SimIm(T5.AP, p=0.10)

T5.TR1.10<-SimIm(T5.TR, p=0.10)
T5.TR2.10<-SimIm(T5.TR, p=0.10)
T5.TR3.10<-SimIm(T5.TR, p=0.10)
T5.TR4.10<-SimIm(T5.TR, p=0.10)
T5.TR5.10<-SimIm(T5.TR, p=0.10)

T10.AP1.10<-SimIm(T10.AP, p=0.10)
T10.AP2.10<-SimIm(T10.AP, p=0.10)
T10.AP3.10<-SimIm(T10.AP, p=0.10)
T10.AP4.10<-SimIm(T10.AP, p=0.10)
T10.AP5.10<-SimIm(T10.AP, p=0.10)

T10.TR1.10<-SimIm(T10.TR, p=0.10)
T10.TR2.10<-SimIm(T10.TR, p=0.10)
T10.TR3.10<-SimIm(T10.TR, p=0.10)
T10.TR4.10<-SimIm(T10.TR, p=0.10)
T10.TR5.10<-SimIm(T10.TR, p=0.10)

L1.AP1.10<-SimIm(L1.AP, p=0.10)
L1.AP2.10<-SimIm(L1.AP, p=0.10)
L1.AP3.10<-SimIm(L1.AP, p=0.10)
L1.AP4.10<-SimIm(L1.AP, p=0.10)
L1.AP5.10<-SimIm(L1.AP, p=0.10)

L1.TR1.10<-SimIm(L1.TR, p=0.10)
L1.TR2.10<-SimIm(L1.TR, p=0.10)
L1.TR3.10<-SimIm(L1.TR, p=0.10)
L1.TR4.10<-SimIm(L1.TR, p=0.10)
L1.TR5.10<-SimIm(L1.TR, p=0.10)

L3.AP1.10<-SimIm(L3.AP, p=0.10)
L3.AP2.10<-SimIm(L3.AP, p=0.10)
L3.AP3.10<-SimIm(L3.AP, p=0.10)
L3.AP4.10<-SimIm(L3.AP, p=0.10)
L3.AP5.10<-SimIm(L3.AP, p=0.10)

L3.TR1.10<-SimIm(L3.TR, p=0.10)
L3.TR2.10<-SimIm(L3.TR, p=0.10)
L3.TR3.10<-SimIm(L3.TR, p=0.10)
L3.TR4.10<-SimIm(L3.TR, p=0.10)
L3.TR5.10<-SimIm(L3.TR, p=0.10)
```


Making 20% missing data
```{r}
FL.L1.20<-SimIm(FL_L, p=0.20)
FL.L2.20<-SimIm(FL_L, p=0.20)
FL.L3.20<-SimIm(FL_L, p=0.20)
FL.L4.20<-SimIm(FL_L, p=0.20)
FL.L5.20<-SimIm(FL_L, p=0.20)

FL.R1.20<-SimIm(FL_R, p=0.20)
FL.R2.20<-SimIm(FL_R, p=0.20)
FL.R3.20<-SimIm(FL_R, p=0.20)
FL.R4.20<-SimIm(FL_R, p=0.20)
FL.R5.20<-SimIm(FL_R, p=0.20)

T1.AP1.20<-SimIm(T1.AP, p=0.20)
T1.AP2.20<-SimIm(T1.AP, p=0.20)
T1.AP3.20<-SimIm(T1.AP, p=0.20)
T1.AP4.20<-SimIm(T1.AP, p=0.20)
T1.AP5.20<-SimIm(T1.AP, p=0.20)

T1.TR1.20<-SimIm(T1.TR, p=0.20)
T1.TR2.20<-SimIm(T1.TR, p=0.20)
T1.TR3.20<-SimIm(T1.TR, p=0.20)
T1.TR4.20<-SimIm(T1.TR, p=0.20)
T1.TR5.20<-SimIm(T1.TR, p=0.20)

T5.AP1.20<-SimIm(T5.AP, p=0.20)
T5.AP2.20<-SimIm(T5.AP, p=0.20)
T5.AP3.20<-SimIm(T5.AP, p=0.20)
T5.AP4.20<-SimIm(T5.AP, p=0.20)
T5.AP5.20<-SimIm(T5.AP, p=0.20)

T5.TR1.20<-SimIm(T5.TR, p=0.20)
T5.TR2.20<-SimIm(T5.TR, p=0.20)
T5.TR3.20<-SimIm(T5.TR, p=0.20)
T5.TR4.20<-SimIm(T5.TR, p=0.20)
T5.TR5.20<-SimIm(T5.TR, p=0.20)

T10.AP1.20<-SimIm(T10.AP, p=0.20)
T10.AP2.20<-SimIm(T10.AP, p=0.20)
T10.AP3.20<-SimIm(T10.AP, p=0.20)
T10.AP4.20<-SimIm(T10.AP, p=0.20)
T10.AP5.20<-SimIm(T10.AP, p=0.20)

T10.TR1.20<-SimIm(T10.TR, p=0.20)
T10.TR2.20<-SimIm(T10.TR, p=0.20)
T10.TR3.20<-SimIm(T10.TR, p=0.20)
T10.TR4.20<-SimIm(T10.TR, p=0.20)
T10.TR5.20<-SimIm(T10.TR, p=0.20)

L1.AP1.20<-SimIm(L1.AP, p=0.20)
L1.AP2.20<-SimIm(L1.AP, p=0.20)
L1.AP3.20<-SimIm(L1.AP, p=0.20)
L1.AP4.20<-SimIm(L1.AP, p=0.20)
L1.AP5.20<-SimIm(L1.AP, p=0.20)

L1.TR1.20<-SimIm(L1.TR, p=0.20)
L1.TR2.20<-SimIm(L1.TR, p=0.20)
L1.TR3.20<-SimIm(L1.TR, p=0.20)
L1.TR4.20<-SimIm(L1.TR, p=0.20)
L1.TR5.20<-SimIm(L1.TR, p=0.20)

L3.AP1.20<-SimIm(L3.AP, p=0.20)
L3.AP2.20<-SimIm(L3.AP, p=0.20)
L3.AP3.20<-SimIm(L3.AP, p=0.20)
L3.AP4.20<-SimIm(L3.AP, p=0.20)
L3.AP5.20<-SimIm(L3.AP, p=0.20)

L3.TR1.20<-SimIm(L3.TR, p=0.20)
L3.TR2.20<-SimIm(L3.TR, p=0.20)
L3.TR3.20<-SimIm(L3.TR, p=0.20)
L3.TR4.20<-SimIm(L3.TR, p=0.20)
L3.TR5.20<-SimIm(L3.TR, p=0.20)
```

Making 30% missing data
```{r}
FL.L1.30<-SimIm(FL_L, p=0.30)
FL.L2.30<-SimIm(FL_L, p=0.30)
FL.L3.30<-SimIm(FL_L, p=0.30)
FL.L4.30<-SimIm(FL_L, p=0.30)
FL.L5.30<-SimIm(FL_L, p=0.30)

FL.R1.30<-SimIm(FL_R, p=0.30)
FL.R2.30<-SimIm(FL_R, p=0.30)
FL.R3.30<-SimIm(FL_R, p=0.30)
FL.R4.30<-SimIm(FL_R, p=0.30)
FL.R5.30<-SimIm(FL_R, p=0.30)

T1.AP1.30<-SimIm(T1.AP, p=0.30)
T1.AP2.30<-SimIm(T1.AP, p=0.30)
T1.AP3.30<-SimIm(T1.AP, p=0.30)
T1.AP4.30<-SimIm(T1.AP, p=0.30)
T1.AP5.30<-SimIm(T1.AP, p=0.30)

T1.TR1.30<-SimIm(T1.TR, p=0.30)
T1.TR2.30<-SimIm(T1.TR, p=0.30)
T1.TR3.30<-SimIm(T1.TR, p=0.30)
T1.TR4.30<-SimIm(T1.TR, p=0.30)
T1.TR5.30<-SimIm(T1.TR, p=0.30)

T5.AP1.30<-SimIm(T5.AP, p=0.30)
T5.AP2.30<-SimIm(T5.AP, p=0.30)
T5.AP3.30<-SimIm(T5.AP, p=0.30)
T5.AP4.30<-SimIm(T5.AP, p=0.30)
T5.AP5.30<-SimIm(T5.AP, p=0.30)

T5.TR1.30<-SimIm(T5.TR, p=0.30)
T5.TR2.30<-SimIm(T5.TR, p=0.30)
T5.TR3.30<-SimIm(T5.TR, p=0.30)
T5.TR4.30<-SimIm(T5.TR, p=0.30)
T5.TR5.30<-SimIm(T5.TR, p=0.30)

T10.AP1.30<-SimIm(T10.AP, p=0.30)
T10.AP2.30<-SimIm(T10.AP, p=0.30)
T10.AP3.30<-SimIm(T10.AP, p=0.30)
T10.AP4.30<-SimIm(T10.AP, p=0.30)
T10.AP5.30<-SimIm(T10.AP, p=0.30)

T10.TR1.30<-SimIm(T10.TR, p=0.30)
T10.TR2.30<-SimIm(T10.TR, p=0.30)
T10.TR3.30<-SimIm(T10.TR, p=0.30)
T10.TR4.30<-SimIm(T10.TR, p=0.30)
T10.TR5.30<-SimIm(T10.TR, p=0.30)

L1.AP1.30<-SimIm(L1.AP, p=0.30)
L1.AP2.30<-SimIm(L1.AP, p=0.30)
L1.AP3.30<-SimIm(L1.AP, p=0.30)
L1.AP4.30<-SimIm(L1.AP, p=0.30)
L1.AP5.30<-SimIm(L1.AP, p=0.30)

L1.TR1.30<-SimIm(L1.TR, p=0.30)
L1.TR2.30<-SimIm(L1.TR, p=0.30)
L1.TR3.30<-SimIm(L1.TR, p=0.30)
L1.TR4.30<-SimIm(L1.TR, p=0.30)
L1.TR5.30<-SimIm(L1.TR, p=0.30)

L3.AP1.30<-SimIm(L3.AP, p=0.30)
L3.AP2.30<-SimIm(L3.AP, p=0.30)
L3.AP3.30<-SimIm(L3.AP, p=0.30)
L3.AP4.30<-SimIm(L3.AP, p=0.30)
L3.AP5.30<-SimIm(L3.AP, p=0.30)

L3.TR1.30<-SimIm(L3.TR, p=0.30)
L3.TR2.30<-SimIm(L3.TR, p=0.30)
L3.TR3.30<-SimIm(L3.TR, p=0.30)
L3.TR4.30<-SimIm(L3.TR, p=0.30)
L3.TR5.30<-SimIm(L3.TR, p=0.30)
```

Making 40% missing data
```{r}
FL.L1.40<-SimIm(FL_L, p=0.40)
FL.L2.40<-SimIm(FL_L, p=0.40)
FL.L3.40<-SimIm(FL_L, p=0.40)
FL.L4.40<-SimIm(FL_L, p=0.40)
FL.L5.40<-SimIm(FL_L, p=0.40)

FL.R1.40<-SimIm(FL_R, p=0.40)
FL.R2.40<-SimIm(FL_R, p=0.40)
FL.R3.40<-SimIm(FL_R, p=0.40)
FL.R4.40<-SimIm(FL_R, p=0.40)
FL.R5.40<-SimIm(FL_R, p=0.40)

T1.AP1.40<-SimIm(T1.AP, p=0.40)
T1.AP2.40<-SimIm(T1.AP, p=0.40)
T1.AP3.40<-SimIm(T1.AP, p=0.40)
T1.AP4.40<-SimIm(T1.AP, p=0.40)
T1.AP5.40<-SimIm(T1.AP, p=0.40)

T1.TR1.40<-SimIm(T1.TR, p=0.40)
T1.TR2.40<-SimIm(T1.TR, p=0.40)
T1.TR3.40<-SimIm(T1.TR, p=0.40)
T1.TR4.40<-SimIm(T1.TR, p=0.40)
T1.TR5.40<-SimIm(T1.TR, p=0.40)

T5.AP1.40<-SimIm(T5.AP, p=0.40)
T5.AP2.40<-SimIm(T5.AP, p=0.40)
T5.AP3.40<-SimIm(T5.AP, p=0.40)
T5.AP4.40<-SimIm(T5.AP, p=0.40)
T5.AP5.40<-SimIm(T5.AP, p=0.40)

T5.TR1.40<-SimIm(T5.TR, p=0.40)
T5.TR2.40<-SimIm(T5.TR, p=0.40)
T5.TR3.40<-SimIm(T5.TR, p=0.40)
T5.TR4.40<-SimIm(T5.TR, p=0.40)
T5.TR5.40<-SimIm(T5.TR, p=0.40)

T10.AP1.40<-SimIm(T10.AP, p=0.40)
T10.AP2.40<-SimIm(T10.AP, p=0.40)
T10.AP.40<-SimIm(T10.AP, p=0.40)
T10.AP4.40<-SimIm(T10.AP, p=0.40)
T10.AP5.40<-SimIm(T10.AP, p=0.40)

T10.TR1.40<-SimIm(T10.TR, p=0.40)
T10.TR2.40<-SimIm(T10.TR, p=0.40)
T10.TR3.40<-SimIm(T10.TR, p=0.40)
T10.TR4.40<-SimIm(T10.TR, p=0.40)
T10.TR5.40<-SimIm(T10.TR, p=0.40)

L1.AP1.40<-SimIm(L1.AP, p=0.40)
L1.AP2.40<-SimIm(L1.AP, p=0.40)
L1.AP3.40<-SimIm(L1.AP, p=0.40)
L1.AP4.40<-SimIm(L1.AP, p=0.40)
L1.AP5.40<-SimIm(L1.AP, p=0.40)

L1.TR1.40<-SimIm(L1.TR, p=0.40)
L1.TR2.40<-SimIm(L1.TR, p=0.40)
L1.TR3.40<-SimIm(L1.TR, p=0.40)
L1.TR4.40<-SimIm(L1.TR, p=0.40)
L1.TR5.40<-SimIm(L1.TR, p=0.40)

L3.AP1.40<-SimIm(L3.AP, p=0.40)
L3.AP2.40<-SimIm(L3.AP, p=0.40)
L3.AP3.40<-SimIm(L3.AP, p=0.40)
L3.AP4.40<-SimIm(L3.AP, p=0.40)
L3.AP5.40<-SimIm(L3.AP, p=0.40)

L3.TR1.40<-SimIm(L3.TR, p=0.40)
L3.TR2.40<-SimIm(L3.TR, p=0.40)
L3.TR3.40<-SimIm(L3.TR, p=0.40)
L3.TR4.40<-SimIm(L3.TR, p=0.40)
L3.TR5.40<-SimIm(L3.TR, p=0.40)
```

#######################
Combining the variables
#######################

Now we must combine the columns created above back into 5 dataframes for each missing data percentage - 25 total.


```{r}
cont.ten.1<-cbind(FL.L1.05, FL.R1.05, T1.AP1.05, T1.TR1.05, T5.AP1.05, T5.TR1.05, T10.AP1.05, T10.TR1.05, L1.AP1.05, L1.TR1.05, L3.AP1.05, L3.TR1.05)
cont.ten.2<-cbind(FL.L2.05, FL.R2.05, T1.AP2.05, T1.TR2.05, T5.AP2.05, T5.TR2.05, T10.AP2.05, T10.TR2.05, L1.AP2.05, L1.TR2.05, L3.AP2.05, L3.TR2.05)
cont.ten.3<-cbind(FL.L3.05, FL.R3.05, T1.AP3.05, T1.TR3.05, T5.AP3.05, T5.TR3.05, T10.AP3.05, T10.TR3.05, L1.AP3.05, L1.TR3.05, L3.AP3.05, L3.TR3.05)
cont.ten.4<-cbind(FL.L4.05, FL.R4.05, T1.AP4.05, T1.TR4.05, T5.AP4.05, T5.TR4.05, T10.AP4.05, T10.TR4.05, L1.AP4.05, L1.TR4.05, L3.AP4.05, L3.TR4.05)
cont.ten.5<-cbind(FL.L5.05, FL.R5.05, T1.AP5.05, T1.TR5.05, T5.AP5.05, T5.TR5.05, T10.AP5.05, T10.TR5.05, L1.AP5.05, L1.TR5.05, L3.AP5.05, L3.TR5.05)
```

Now compiling 5 versions of 10%
```{r}
cont.five.1<-cbind(FL.L1.10, FL.R1.10, T1.AP1.10, T1.TR1.10, T5.AP1.10, T5.TR1.10, T10.AP1.10, T10.TR1.10, L1.AP1.10, L1.TR1.10, L3.AP1.10, L3.TR1.10)
cont.five.2<-cbind(FL.L2.10, FL.R2.10, T1.AP2.10, T1.TR2.10, T5.AP2.10, T5.TR2.10, T10.AP2.10, T10.TR2.10, L1.AP2.10, L1.TR2.10, L3.AP2.10, L3.TR2.10)
cont.five.3<-cbind(FL.L3.10, FL.R3.10, T1.AP3.10, T1.TR3.10, T5.AP3.10, T5.TR3.10, T10.AP3.10, T10.TR3.10, L1.AP3.10, L1.TR3.10, L3.AP3.10, L3.TR3.10)
cont.five.4<-cbind(FL.L4.10, FL.R4.10, T1.AP4.10, T1.TR4.10, T5.AP4.10, T5.TR4.10, T10.AP4.10, T10.TR4.10, L1.AP4.10, L1.TR4.10, L3.AP4.10, L3.TR4.10)
cont.five.5<-cbind(FL.L5.10, FL.R5.10, T1.AP5.10, T1.TR5.10, T5.AP5.10, T5.TR5.10, T10.AP5.10, T10.TR5.10, L1.AP5.10, L1.TR5.10, L3.AP5.10, L3.TR5.10)
```

Now compiling 5 versions of 20%
```{r}
cont.twenty.1<-cbind(FL.L1.20, FL.R1.20, T1.AP1.20, T1.TR1.20, T5.AP1.20, T5.TR1.20, T10.AP1.20, T10.TR1.20, L1.AP1.20, L1.TR1.20, L3.AP1.20, L3.TR1.20)
cont.twenty.2<-cbind(FL.L2.20, FL.R2.20, T1.AP2.20, T1.TR2.20, T5.AP2.20, T5.TR2.20, T10.AP2.20, T10.TR2.20, L1.AP2.20, L1.TR2.20, L3.AP2.20, L3.TR2.20)
cont.twenty.3<-cbind(FL.L3.20, FL.R3.20, T1.AP3.20, T1.TR3.20, T5.AP3.20, T5.TR3.20, T10.AP3.20, T10.TR3.20, L1.AP3.20, L1.TR3.20, L3.AP3.20, L3.TR3.20)
cont.twenty.4<-cbind(FL.L4.20, FL.R4.20, T1.AP4.20, T1.TR4.20, T5.AP4.20, T5.TR4.20, T10.AP4.20, T10.TR4.20, L1.AP4.20, L1.TR4.20, L3.AP4.20, L3.TR4.20)
cont.twenty.5<-cbind(FL.L5.20, FL.R5.20, T1.AP5.20, T1.TR5.20, T5.AP5.20, T5.TR5.20, T10.AP5.20, T10.TR5.20, L1.AP5.20, L1.TR5.20, L3.AP5.20, L3.TR5.20)
```

Now compiling 5 versions of 30%
```{r}
cont.thirty.1<-cbind(FL.L1.30, FL.R1.30, T1.AP1.30, T1.TR1.30, T5.AP1.30, T5.TR1.30, T10.AP1.30, T10.TR1.30, L1.AP1.30, L1.TR1.30, L3.AP1.30, L3.TR1.30)
cont.thirty.2<-cbind(FL.L2.30, FL.R2.30, T1.AP2.30, T1.TR2.30, T5.AP2.30, T5.TR2.30, T10.AP2.30, T10.TR2.30, L1.AP2.30, L1.TR2.30, L3.AP2.30, L3.TR2.30)
cont.thirty.3<-cbind(FL.L3.30, FL.R3.30, T1.AP3.30, T1.TR3.30, T5.AP3.30, T5.TR3.30, T10.AP3.30, T10.TR3.30, L1.AP3.30, L1.TR3.30, L3.AP3.30, L3.TR3.30)
cont.thirty.4<-cbind(FL.L4.30, FL.R4.30, T1.AP4.30, T1.TR4.30, T5.AP4.30, T5.TR4.30, T10.AP4.30, T10.TR4.30, L1.AP4.30, L1.TR4.30, L3.AP4.30, L3.TR4.30)
cont.thirty.5<-cbind(FL.L5.30, FL.R5.30, T1.AP5.30, T1.TR5.30, T5.AP5.30, T5.TR5.30, T10.AP5.30, T10.TR5.30, L1.AP5.30, L1.TR5.30, L3.AP5.30, L3.TR5.30)
```

Now compiling 5 versions of 40%
```{r}
cont.forty.1<-cbind(FL.L1.40, FL.R1.40, T1.AP1.40, T1.TR1.40, T5.AP1.40, T5.TR1.40, T10.AP1.40, T10.TR1.40, L1.AP1.40, L1.TR1.40, L3.AP1.40, L3.TR1.40)
cont.forty.2<-cbind(FL.L2.40, FL.R2.40, T1.AP2.40, T1.TR2.40, T5.AP2.40, T5.TR2.40, T10.AP2.40, T10.TR2.40, L1.AP2.40, L1.TR2.40, L3.AP2.40, L3.TR2.40)
cont.forty.3<-cbind(FL.L3.40, FL.R3.40, T1.AP3.40, T1.TR3.40, T5.AP3.40, T5.TR3.40, T10.AP3.40, T10.TR3.40, L1.AP3.40, L1.TR3.40, L3.AP3.40, L3.TR3.40)
cont.forty.4<-cbind(FL.L4.40, FL.R4.40, T1.AP4.40, T1.TR4.40, T5.AP4.40, T5.TR4.40, T10.AP4.40, T10.TR4.40, L1.AP4.40, L1.TR4.40, L3.AP4.40, L3.TR4.40)
cont.forty.5<-cbind(FL.L5.40, FL.R5.40, T1.AP5.40, T1.TR5.40, T5.AP5.40, T5.TR5.40, T10.AP5.40, T10.TR5.40, L1.AP5.40, L1.TR5.40, L3.AP5.40, L3.TR5.40)
```

Take each new data frame and label the columns and export as .csv so they can be used in other analyses
```{r}
colnames(cont.five.1)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.1, file="cont.five.1.csv")

colnames(cont.five.2)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.2, file="cont.five.2.csv")

colnames(cont.five.3)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.3, file="cont.five.3.csv")

colnames(cont.five.4)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.4, file="cont.five.4.csv")

colnames(cont.five.5)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.5, file="cont.five.5.csv")
```


```{r}
colnames(cont.ten.1)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.ten.1, file="cont.ten.1.csv")

colnames(cont.ten.2)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.ten.2, file="cont.ten.2.csv")

colnames(cont.ten.3)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.ten.3, file="cont.ten.3.csv")

colnames(cont.ten.4)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.ten.4, file="cont.ten.4.csv")

colnames(cont.ten.5)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.ten.5, file="cont.ten.5.csv")
```


```{r}
colnames(cont.twenty.1)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.twenty.1, file="cont.twenty.1.csv")

colnames(cont.twenty.2)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.twenty.2, file="cont.twenty.2.csv")

colnames(cont.twenty.3)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.twenty.3, file="cont.twenty.3.csv")

colnames(cont.twenty.4)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.twenty.4, file="cont.twenty.4.csv")

colnames(cont.twenty.5)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.twenty.5, file="cont.twenty.5.csv")
```

```{r}
colnames(cont.thirty.1)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.thirty.1, file="cont.thirty.1.csv")

colnames(cont.thirty.2)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.thirty.2, file="cont.thirty.2.csv")

colnames(cont.thirty.3)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.thirty.3, file="cont.thirty.3.csv")

colnames(cont.thirty.4)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.thirty.4, file="cont.thirty.4.csv")

colnames(cont.thirty.5)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.thirty.5, file="cont.thirty.5.csv")
```


```{r}
colnames(cont.forty.1)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.forty.1, file="cont.forty.1.csv")

colnames(cont.forty.2)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.forty.2, file="cont.forty.2.csv")

colnames(cont.forty.3)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.forty.3, file="cont.forty.3.csv")

colnames(cont.forty.4)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.forty.4, file="cont.forty.4.csv")

colnames(cont.forty.5)<-c("FL_L", "FL_R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.forty.5, file="cont.forty.5.csv")
```

