
####Expectation Maximization Imputation of Continuous variables####

This example uses 5% missingness 

Packages Required: 
1) missMethods  https://cran.r-project.org/web/packages/missMethods/missMethods.pdf
2) hydroGOF  https://cran.r-project.org/web/packages/hydroGOF/hydroGOF.pdf

#STEP 1# Load packages and set working directory
```{r}
library(knitr)
rm(list=ls())

library(missMethods)
library(hydroGOF)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
```

#STEP 2# Load the data

*Practice.Continuous.Dataset.csv* is the complete dataset - i.e. no missing data. The complete dataset is needed in order to evaluate the success of the imputation/deletion method

*cont.five.1.practive.csv* is the first version of the complete dataset that has 5% of the values missing.
*cont.five.2.practice.csv* is the second version of the complete dataset that has 5% of the values missing. Etc. Each of the 5 versions has different values missing.

Having multiple versions ensures that the overall results are not due to random chance. Here, I chose 5 versions, but you could choose 3 or 10 or however many you want. 
```{r}
data<-read.csv("Practice.Continuous.Dataset.csv", header=T)

cont.five.1<-read.csv("cont.five.1.practice.csv", header=T)
cont.five.2<-read.csv("cont.five.2.practice.csv", header=T)
cont.five.3<-read.csv("cont.five.3.practice.csv", header=T)
cont.five.4<-read.csv("cont.five.4.practice.csv", header=T)
cont.five.5<-read.csv("cont.five.5.practice.csv", header=T)
```

#STEP 3# Impute the Data

Use the impute_EM function from missMethods

We create 5 versions of each and average them together

Dataset 1
```{r}
set.seed(1)
EMone1<-impute_EM(cont.five.1, stochastic=TRUE, verbose=TRUE)
EMone2<-impute_EM(cont.five.1, stochastic=TRUE, verbose=TRUE)
EMone3<-impute_EM(cont.five.1, stochastic=TRUE, verbose=TRUE)
EMone4<-impute_EM(cont.five.1, stochastic=TRUE, verbose=TRUE)
EMone5<-impute_EM(cont.five.1, stochastic=TRUE, verbose=TRUE)

EM_imp1<-(EMone1 + EMone2 + EMone3 + EMone4 + EMone5)/5
```

Dataset 2
```{r}
set.seed(1)
EMtwo1<-impute_EM(cont.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo2<-impute_EM(cont.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo3<-impute_EM(cont.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo4<-impute_EM(cont.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo5<-impute_EM(cont.five.2, stochastic=TRUE, verbose=TRUE)

EM_imp2<-(EMtwo1 + EMtwo2 + EMtwo3 + EMtwo4 + EMtwo5)/5
```

Dataset 3
```{r}
set.seed(1)
EMthree1<-impute_EM(cont.five.3, stochastic=TRUE, verbose=TRUE)
EMthree2<-impute_EM(cont.five.3, stochastic=TRUE, verbose=TRUE)
EMthree3<-impute_EM(cont.five.3, stochastic=TRUE, verbose=TRUE)
EMthree4<-impute_EM(cont.five.3, stochastic=TRUE, verbose=TRUE)
EMthree5<-impute_EM(cont.five.3, stochastic=TRUE, verbose=TRUE)

EM_imp3<-(EMthree1 + EMthree2 + EMthree3 + EMthree4 + EMthree5)/5
```

Dataset 4
```{r}
set.seed(1)
EMfour1<-impute_EM(cont.five.4, stochastic=TRUE, verbose=TRUE)
EMfour2<-impute_EM(cont.five.4, stochastic=TRUE, verbose=TRUE)
EMfour3<-impute_EM(cont.five.4, stochastic=TRUE, verbose=TRUE)
EMfour4<-impute_EM(cont.five.4, stochastic=TRUE, verbose=TRUE)
EMfour5<-impute_EM(cont.five.4, stochastic=TRUE, verbose=TRUE)

EM_imp4<-(EMfour1 + EMfour2 + EMfour3 + EMfour4 + EMfour5)/5
```

Dataset 5
```{r}
set.seed(1)
EMfive1<-impute_EM(cont.five.5, stochastic=TRUE, verbose=TRUE)
EMfive2<-impute_EM(cont.five.5, stochastic=TRUE, verbose=TRUE)
EMfive3<-impute_EM(cont.five.5, stochastic=TRUE, verbose=TRUE)
EMfive4<-impute_EM(cont.five.5, stochastic=TRUE, verbose=TRUE)
EMfive5<-impute_EM(cont.five.5, stochastic=TRUE, verbose=TRUE)

EM_imp5<-(EMfive1 + EMfive2 + EMfive3 + EMfive4 + EMfive5)/5
```

#STEP 5# Calculate Success Parameters
Now that we have created 5 imputed datasets, we must assess how close the imputed values are to the original dataset

Here we establish the variable means for the complete dataset so we can calculate the percent error by variable at the end
```{r}
FL.Ldatmean<-mean(data$FL.Left)
FL.Rdatmean<-mean(data$FL.Right)
T1.APdatmean<-mean(data$T1.AP)
T1.TRdatmean<-mean(data$T1.TR)
T5.APdatmean<-mean(data$T5.AP)
T5.TRdatmean<-mean(data$T5.TR)
T10.APdatmean<-mean(data$T10.AP)
T10.TRdatmean<-mean(data$T10.TR)
L1.APdatmean<-mean(data$L1.AP)
L1.TRdatmean<-mean(data$L1.TR)
L3.APdatmean<-mean(data$L3.AP)
L3.TRdatmean<-mean(data$L3.TR)
```

*Prepare Data to calculate Percent Error*
We must combine the means across each of the 5 versions by variable so that we produce a single percent error for each variable at the end. 
```{r}
FL.L.mean.imp<-mean(c(EM_imp1$FL.Left, EM_imp2$FL.Left, EM_imp3$FL.Left, EM_imp4$FL.Left, EM_imp5$FL.Left))
FL.R.mean.imp<-mean(c(EM_imp1$FL.Right, EM_imp2$FL.Right, EM_imp3$FL.Right, EM_imp4$FL.Right, EM_imp5$FL.Right))
T1.AP.mean.imp<-mean(c(EM_imp1$T1.AP, EM_imp2$T1.AP, EM_imp3$T1.AP, EM_imp4$T1.AP, EM_imp5$T1.AP))
T1.TR.mean.imp<-mean(c(EM_imp1$T1.TR, EM_imp2$T1.TR, EM_imp3$T1.TR, EM_imp4$T1.TR, EM_imp5$T1.TR))
T5.AP.mean.imp<-mean(c(EM_imp1$T5.AP, EM_imp2$T5.AP, EM_imp3$T5.AP, EM_imp4$T5.AP, EM_imp5$T5.AP))
T5.TR.mean.imp<-mean(c(EM_imp1$T5.TR, EM_imp2$T5.TR, EM_imp3$T5.TR, EM_imp4$T5.TR, EM_imp5$T5.TR))
T10.AP.mean.imp<-mean(c(EM_imp1$T10.AP, EM_imp2$T10.AP, EM_imp3$T10.AP, EM_imp4$T10.AP, EM_imp5$T10.AP))
T10.TR.mean.imp<-mean(c(EM_imp1$T10.TR, EM_imp2$T10.TR, EM_imp3$T10.TR, EM_imp4$T10.TR, EM_imp5$T10.TR))
L1.AP.mean.imp<-mean(c(EM_imp1$L1.AP, EM_imp2$L1.AP, EM_imp3$L1.AP, EM_imp4$L1.AP, EM_imp5$L1.AP))
L1.TR.mean.imp<-mean(c(EM_imp1$L1.TR, EM_imp2$L1.TR, EM_imp3$L1.TR, EM_imp4$L1.TR, EM_imp5$L1.TR))
L3.AP.mean.imp<-mean(c(EM_imp1$L3.AP, EM_imp2$L3.AP, EM_imp3$L3.AP, EM_imp4$L3.AP, EM_imp5$L3.AP))
L3.TR.mean.imp<-mean(c(EM_imp1$L3.TR, EM_imp2$L3.TR, EM_imp3$L3.TR, EM_imp4$L3.TR, EM_imp5$L3.TR))
```

Percent error is the absolute value of the observed value minus the expected value divided by the expected, all multiplied by 100
```{r}
ab<-c((abs((FL.L.mean.imp-FL.Ldatmean)/FL.Ldatmean)*100),(abs((FL.R.mean.imp-FL.Rdatmean)/FL.Rdatmean)*100),(abs((T1.AP.mean.imp-T1.APdatmean)/T1.APdatmean)*100),(abs((T1.TR.mean.imp-T1.TRdatmean)/T1.TRdatmean)*100),(abs((T5.AP.mean.imp-T5.APdatmean)/T5.APdatmean)*100), (abs((T5.TR.mean.imp-T5.TRdatmean)/T5.TRdatmean)*100), (abs((T10.AP.mean.imp-T10.APdatmean)/T10.APdatmean)*100), (abs((T10.TR.mean.imp-T10.TRdatmean)/T10.TRdatmean)*100), (abs((L1.AP.mean.imp-L1.APdatmean)/L1.APdatmean)*100), (abs((L1.TR.mean.imp-L1.TRdatmean)/L1.TRdatmean)*100), (abs((L3.AP.mean.imp-L3.APdatmean)/L3.APdatmean)*100), (abs((L3.TR.mean.imp-L3.TRdatmean)/L3.TRdatmean)*100))

write.csv(ab, file="PE.cont.EM.csv")
```


**Calculate Normalized Root Mean Square Error (NRMSE)**

Use hydroGOF package to assess NRMSE between observed and simulated values for each of the 5 versions of the imputed datasets

#EM_imp1
```{r}
obsA<-c(data$FL.Left)
simA<-c(EM_imp1$FL.Left)
dfA<-as.data.frame(t(gof(sim=simA, obs=obsA)))
A<-dfA$`NRMSE %`

obsB<-c(data$FL.Right)
simB<-c(EM_imp1$FL.Right)
dfB<-as.data.frame(t(gof(sim=simB, obs=obsB)))
B<-dfB$`NRMSE %`

obsC<-c(data$T1.AP)
simC<-c(EM_imp1$T1.AP)
dfC<-as.data.frame(t(gof(sim=simC, obs=obsC)))
C<-dfC$`NRMSE %`

obsD<-c(data$T1.TR)
simD<-c(EM_imp1$T1.TR)
dfD<-as.data.frame(t(gof(sim=simD, obs=obsD)))
D<-dfD$`NRMSE %`

obsE<-c(data$T5.AP)
simE<-c(EM_imp1$T5.AP)
dfE<-as.data.frame(t(gof(sim=simE, obs=obsE)))
E<-dfE$`NRMSE %`

obsF<-c(data$T5.TR)
simF<-c(EM_imp1$T5.TR)
dfF<-as.data.frame(t(gof(sim=simF, obs=obsF)))
F<-dfF$`NRMSE %`

obsG<-c(data$T10.AP)
simG<-c(EM_imp1$T10.AP)
dfG<-as.data.frame(t(gof(sim=simG, obs=obsG)))
G<-dfG$`NRMSE %`

obsH<-c(data$T10.TR)
simH<-c(EM_imp1$T10.TR)
dfH<-as.data.frame(t(gof(sim=simH, obs=obsH)))
H<-dfH$`NRMSE %`

obsI<-c(data$L1.AP)
simI<-c(EM_imp1$L1.AP)
dfI<-as.data.frame(t(gof(sim=simI, obs=obsI)))
I<-dfI$`NRMSE %`

obsJ<-c(data$L1.TR)
simJ<-c(EM_imp1$L1.TR)
dfJ<-as.data.frame(t(gof(sim=simJ, obs=obsJ)))
J<-dfJ$`NRMSE %`

obsK<-c(data$L3.AP)
simK<-c(EM_imp1$L3.AP)
dfK<-as.data.frame(t(gof(sim=simK, obs=obsK)))
K<-dfK$`NRMSE %`

obsL<-c(data$L3.TR)
simL<-c(EM_imp1$L3.TR)
dfL<-as.data.frame(t(gof(sim=simL, obs=obsL)))
L<-dfL$`NRMSE %`
```

#EM_imp2
```{r}
obsAA<-c(data$FL.Left)
simAA<-c(EM_imp2$FL.Left)
dfAA<-as.data.frame(t(gof(sim=simAA, obs=obsAA)))
AA<-dfAA$`NRMSE %`

obsBB<-c(data$FL.Right)
simBB<-c(EM_imp2$FL.Right)
dfBB<-as.data.frame(t(gof(sim=simBB, obs=obsBB)))
BB<-dfBB$`NRMSE %`

obsCC<-c(data$T1.AP)
simCC<-c(EM_imp2$T1.AP)
dfCC<-as.data.frame(t(gof(sim=simCC, obs=obsCC)))
CC<-dfCC$`NRMSE %`

obsDD<-c(data$T1.TR)
simDD<-c(EM_imp2$T1.TR)
dfDD<-as.data.frame(t(gof(sim=simDD, obs=obsDD)))
DD<-dfDD$`NRMSE %`

obsEE<-c(data$T5.AP)
simEE<-c(EM_imp2$T5.AP)
dfEE<-as.data.frame(t(gof(sim=simEE, obs=obsEE)))
EE<-dfEE$`NRMSE %`

obsFF<-c(data$T5.TR)
simFF<-c(EM_imp2$T5.TR)
dfFF<-as.data.frame(t(gof(sim=simFF, obs=obsFF)))
FF<-dfFF$`NRMSE %`

obsGG<-c(data$T10.AP)
simGG<-c(EM_imp2$T10.AP)
dfGG<-as.data.frame(t(gof(sim=simGG, obs=obsGG)))
GG<-dfGG$`NRMSE %`

obsHH<-c(data$T10.TR)
simHH<-c(EM_imp2$T10.TR)
dfHH<-as.data.frame(t(gof(sim=simHH, obs=obsHH)))
HH<-dfHH$`NRMSE %`

obsII<-c(data$L1.AP)
simII<-c(EM_imp2$L1.AP)
dfII<-as.data.frame(t(gof(sim=simII, obs=obsII)))
II<-dfII$`NRMSE %`

obsJJ<-c(data$L1.TR)
simJJ<-c(EM_imp2$L1.TR)
dfJJ<-as.data.frame(t(gof(sim=simJJ, obs=obsJJ)))
JJ<-dfJJ$`NRMSE %`

obsKK<-c(data$L3.AP)
simKK<-c(EM_imp2$L3.AP)
dfKK<-as.data.frame(t(gof(sim=simKK, obs=obsKK)))
KK<-dfKK$`NRMSE %`

obsLL<-c(data$L3.TR)
simLL<-c(EM_imp2$L3.TR)
dfLL<-as.data.frame(t(gof(sim=simLL, obs=obsLL)))
LL<-dfLL$`NRMSE %`
```

#EM_imp3
```{r}
obsAAA<-c(data$FL.Left)
simAAA<-c(EM_imp3$FL.Left)
dfAAA<-as.data.frame(t(gof(sim=simAAA, obs=obsAAA)))
AAA<-dfAAA$`NRMSE %`

obsBBB<-c(data$FL.Right)
simBBB<-c(EM_imp3$FL.Right)
dfBBB<-as.data.frame(t(gof(sim=simBBB, obs=obsBBB)))
BBB<-dfBBB$`NRMSE %`

obsCCC<-c(data$T1.AP)
simCCC<-c(EM_imp3$T1.AP)
dfCCC<-as.data.frame(t(gof(sim=simCCC, obs=obsCCC)))
CCC<-dfCCC$`NRMSE %`

obsDDD<-c(data$T1.TR)
simDDD<-c(EM_imp3$T1.TR)
dfDDD<-as.data.frame(t(gof(sim=simDDD, obs=obsDDD)))
DDD<-dfDDD$`NRMSE %`

obsEEE<-c(data$T5.AP)
simEEE<-c(EM_imp3$T5.AP)
dfEEE<-as.data.frame(t(gof(sim=simEEE, obs=obsEEE)))
EEE<-dfEEE$`NRMSE %`

obsFFF<-c(data$T5.TR)
simFFF<-c(EM_imp3$T5.TR)
dfFFF<-as.data.frame(t(gof(sim=simFFF, obs=obsFFF)))
FFF<-dfFFF$`NRMSE %`

obsGGG<-c(data$T10.AP)
simGGG<-c(EM_imp3$T10.AP)
dfGGG<-as.data.frame(t(gof(sim=simGGG, obs=obsGGG)))
GGG<-dfGGG$`NRMSE %`

obsHHH<-c(data$T10.TR)
simHHH<-c(EM_imp3$T10.TR)
dfHHH<-as.data.frame(t(gof(sim=simHHH, obs=obsHHH)))
HHH<-dfHHH$`NRMSE %`

obsIII<-c(data$L1.AP)
simIII<-c(EM_imp3$L1.AP)
dfIII<-as.data.frame(t(gof(sim=simIII, obs=obsIII)))
III<-dfIII$`NRMSE %`

obsJJJ<-c(data$L1.TR)
simJJJ<-c(EM_imp3$L1.TR)
dfJJJ<-as.data.frame(t(gof(sim=simJJJ, obs=obsJJJ)))
JJJ<-dfJJJ$`NRMSE %`

obsKKK<-c(data$L3.AP)
simKKK<-c(EM_imp3$L3.AP)
dfKKK<-as.data.frame(t(gof(sim=simKKK, obs=obsKKK)))
KKK<-dfKKK$`NRMSE %`

obsLLL<-c(data$L3.TR)
simLLL<-c(EM_imp3$L3.TR)
dfLLL<-as.data.frame(t(gof(sim=simLLL, obs=obsLLL)))
LLL<-dfLLL$`NRMSE %`
```

#EM_imp4
```{r}
obsAAAA<-c(data$FL.Left)
simAAAA<-c(EM_imp4$FL.Left)
dfAAAA<-as.data.frame(t(gof(sim=simAAAA, obs=obsAAAA)))
AAAA<-dfAAAA$`NRMSE %`

obsBBBB<-c(data$FL.Right)
simBBBB<-c(EM_imp4$FL.Right)
dfBBBB<-as.data.frame(t(gof(sim=simBBBB, obs=obsBBBB)))
BBBB<-dfBBBB$`NRMSE %`

obsCCCC<-c(data$T1.AP)
simCCCC<-c(EM_imp4$T1.AP)
dfCCCC<-as.data.frame(t(gof(sim=simCCCC, obs=obsCCCC)))
CCCC<-dfCCCC$`NRMSE %`

obsDDDD<-c(data$T1.TR)
simDDDD<-c(EM_imp4$T1.TR)
dfDDDD<-as.data.frame(t(gof(sim=simDDDD, obs=obsDDDD)))
DDDD<-dfDDDD$`NRMSE %`

obsEEEE<-c(data$T5.AP)
simEEEE<-c(EM_imp4$T5.AP)
dfEEEE<-as.data.frame(t(gof(sim=simEEEE, obs=obsEEEE)))
EEEE<-dfEEEE$`NRMSE %`

obsFFFF<-c(data$T5.TR)
simFFFF<-c(EM_imp4$T5.TR)
dfFFFF<-as.data.frame(t(gof(sim=simFFFF, obs=obsFFFF)))
FFFF<-dfFFFF$`NRMSE %`

obsGGGG<-c(data$T10.AP)
simGGGG<-c(EM_imp4$T10.AP)
dfGGGG<-as.data.frame(t(gof(sim=simGGGG, obs=obsGGGG)))
GGGG<-dfGGGG$`NRMSE %`

obsHHHH<-c(data$T10.TR)
simHHHH<-c(EM_imp4$T10.TR)
dfHHHH<-as.data.frame(t(gof(sim=simHHHH, obs=obsHHHH)))
HHHH<-dfHHHH$`NRMSE %`

obsIIII<-c(data$L1.AP)
simIIII<-c(EM_imp4$L1.AP)
dfIIII<-as.data.frame(t(gof(sim=simIIII, obs=obsIIII)))
IIII<-dfIIII$`NRMSE %`

obsJJJJ<-c(data$L1.TR)
simJJJJ<-c(EM_imp4$L1.TR)
dfJJJJ<-as.data.frame(t(gof(sim=simJJJJ, obs=obsJJJJ)))
JJJJ<-dfJJJJ$`NRMSE %`

obsKKKK<-c(data$L3.AP)
simKKKK<-c(EM_imp4$L3.AP)
dfKKKK<-as.data.frame(t(gof(sim=simKKKK, obs=obsKKKK)))
KKKK<-dfKKKK$`NRMSE %`

obsLLLL<-c(data$L3.TR)
simLLLL<-c(EM_imp4$L3.TR)
dfLLLL<-as.data.frame(t(gof(sim=simLLLL, obs=obsLLLL)))
LLLL<-dfLLLL$`NRMSE %`
```

#EM_imp5
```{r}
obsAAAAA<-c(data$FL.Left)
simAAAAA<-c(EM_imp5$FL.Left)
dfAAAAA<-as.data.frame(t(gof(sim=simAAAAA, obs=obsAAAAA)))
AAAAA<-dfAAAAA$`NRMSE %`

obsBBBBB<-c(data$FL.Right)
simBBBBB<-c(EM_imp5$FL.Right)
dfBBBBB<-as.data.frame(t(gof(sim=simBBBBB, obs=obsBBBBB)))
BBBBB<-dfBBBBB$`NRMSE %`

obsCCCCC<-c(data$T1.AP)
simCCCCC<-c(EM_imp5$T1.AP)
dfCCCCC<-as.data.frame(t(gof(sim=simCCCCC, obs=obsCCCCC)))
CCCCC<-dfCCCCC$`NRMSE %`

obsDDDDD<-c(data$T1.TR)
simDDDDD<-c(EM_imp5$T1.TR)
dfDDDDD<-as.data.frame(t(gof(sim=simDDDDD, obs=obsDDDDD)))
DDDDD<-dfDDDDD$`NRMSE %`

obsEEEEE<-c(data$T5.AP)
simEEEEE<-c(EM_imp5$T5.AP)
dfEEEEE<-as.data.frame(t(gof(sim=simEEEEE, obs=obsEEEEE)))
EEEEE<-dfEEEEE$`NRMSE %`

obsFFFFF<-c(data$T5.TR)
simFFFFF<-c(EM_imp5$T5.TR)
dfFFFFF<-as.data.frame(t(gof(sim=simFFFFF, obs=obsFFFFF)))
FFFFF<-dfFFFFF$`NRMSE %`

obsGGGGG<-c(data$T10.AP)
simGGGGG<-c(EM_imp5$T10.AP)
dfGGGGG<-as.data.frame(t(gof(sim=simGGGGG, obs=obsGGGGG)))
GGGGG<-dfGGGGG$`NRMSE %`

obsHHHHH<-c(data$T10.TR)
simHHHHH<-c(EM_imp5$T10.TR)
dfHHHHH<-as.data.frame(t(gof(sim=simHHHHH, obs=obsHHHHH)))
HHHHH<-dfHHHHH$`NRMSE %`

obsIIIII<-c(data$L1.AP)
simIIIII<-c(EM_imp5$L1.AP)
dfIIIII<-as.data.frame(t(gof(sim=simIIIII, obs=obsIIIII)))
IIIII<-dfIIIII$`NRMSE %`

obsJJJJJ<-c(data$L1.TR)
simJJJJJ<-c(EM_imp5$L1.TR)
dfJJJJJ<-as.data.frame(t(gof(sim=simJJJJJ, obs=obsJJJJJ)))
JJJJJ<-dfJJJJJ$`NRMSE %`

obsKKKKK<-c(data$L3.AP)
simKKKKK<-c(EM_imp5$L3.AP)
dfKKKKK<-as.data.frame(t(gof(sim=simKKKKK, obs=obsKKKKK)))
KKKKK<-dfKKKKK$`NRMSE %`

obsLLLLL<-c(data$L3.TR)
simLLLLL<-c(EM_imp5$L3.TR)
dfLLLLL<-as.data.frame(t(gof(sim=simLLLLL, obs=obsLLLLL)))
LLLLL<-dfLLLLL$`NRMSE %`
```

Put each NRMSE into a matrix to create a usable dataframe that can be exported to Excel
```{r}
aa<-matrix(c(A, B, C, D, E, F, G, H, I, J, K, L), 1, 12)

ab<-matrix(c(AA, BB, CC, DD, EE, FF, GG, HH, II, JJ, KK, LL), 1, 12)

ac<-matrix(c(AAA, BBB, CCC, DDD, EEE, FFF, GGG, HH, III, JJJ, KKK, LLL), 1, 12)

ad<-matrix(c(AAAA, BBBB, CCCC, DDDD, EEEE, FFFF, GGGG, HHHH, IIII, JJJJ, KKKK, LLLL), 1, 12)

ae<-matrix(c(AAAAA, BBBBB, CCCCC, DDDDD, EEEEE, FFFFF, GGGGG, HHHHH, IIIII, JJJJJ, KKKKK, LLLLL), 1, 12)

df.cont.pmm<-data.frame(rbind(aa, ab, ac, ad, ae))
colnames(df.cont.pmm)<-c("FL.Left", "FL.Right", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
rownames(df.cont.pmm)<-c("EM_imp1", "EM_imp2", "EM_imp3", "EM_imp4", "EM_imp5")
write.csv(df.cont.pmm, file="nrmse.continuous.EM.csv")
```