####Random Forest Imputation of Ordinal variables####

This example uses 5% missingness 

Packages Required: 
1) missMethods  https://cran.r-project.org/web/packages/missMethods/missMethods.pdf
2) hydroGOF  https://cran.r-project.org/web/packages/hydroGOF/hydroGOF.pdf

#STEP 1# Load packages and set working directory
```{r}
library(knitr)
rm(list=ls())

library(missForest)
library(hydroGOF)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
```

#STEP 2# Load the data

*Practice.Ordinal.Dataset.csv* is the complete dataset - i.e. no missing data. The complete dataset is needed in order to evaluate the success of the imputation/deletion method

*ord.five.1.practive.csv* is the first version of the complete dataset that has 5% of the values missing.
*ord.five.2.practice.csv* is the second version of the complete dataset that has 5% of the values missing. Etc. Each of the 5 versions has different values missing.

Having multiple versions ensures that the overall results are not due to random chance. Here, I chose 5 versions, but you could choose 3 or 10 or however many you want. 
```{r}
data<-read.csv("Practice.Ordinal.Dataset.csv", header=T)

ord.five.1<-read.csv("ord.five.1.practice.csv", header=T)
ord.five.2<-read.csv("ord.five.2.practice.csv", header=T)
ord.five.3<-read.csv("ord.five.3.practice.csv", header=T)
ord.five.4<-read.csv("ord.five.4.practice.csv", header=T)
ord.five.5<-read.csv("ord.five.5.practice.csv", header=T)
```

#STEP 3# Impute the Data

#Impute the data using missForest package
*maxiter=10* refers to the maximum number of iterations to be performed
*ntree=200* refers to the number of trees to grow
*verbose=FALSE"* if TRUE more information is produced between each iteration
*replace=TRUE* If 'TRUE' bootstrap sampling (with replacements) is performed
*one1* = this is not the FINAL output so I name the output something temporary

NOTE: If you are imputing ordinal paleopathology data that have a only a few possible values you will receive a string of error messages asking "The response has five or fewer unique values.  Are you sure you want to do regression?" The imputation will run anyway. 

```{r}
set.seed(0)
one1<-missForest(ord.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one2<-missForest(ord.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one3<-missForest(ord.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one4<-missForest(ord.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one5<-missForest(ord.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(1)
two1<-missForest(ord.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two2<-missForest(ord.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two3<-missForest(ord.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two4<-missForest(ord.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two5<-missForest(ord.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(2)
three1<-missForest(ord.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three2<-missForest(ord.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three3<-missForest(ord.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three4<-missForest(ord.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three5<-missForest(ord.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(3)
four1<-missForest(ord.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four2<-missForest(ord.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four3<-missForest(ord.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four4<-missForest(ord.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four5<-missForest(ord.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(4)
five1<-missForest(ord.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five2<-missForest(ord.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five3<-missForest(ord.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five4<-missForest(ord.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five5<-missForest(ord.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
```

Extract the completed dataframes from the list
```{r}
one_imp1<-one1$ximp
one_imp2<-one2$ximp
one_imp3<-one3$ximp
one_imp4<-one4$ximp
one_imp5<-one5$ximp

two_imp1<-two1$ximp
two_imp2<-two2$ximp
two_imp3<-two3$ximp
two_imp4<-two4$ximp
two_imp5<-two5$ximp

three_imp1<-three1$ximp
three_imp2<-three2$ximp
three_imp3<-three3$ximp
three_imp4<-three4$ximp
three_imp5<-three5$ximp

four_imp1<-four1$ximp
four_imp2<-four2$ximp
four_imp3<-four3$ximp
four_imp4<-four4$ximp
four_imp5<-four5$ximp

five_imp1<-five1$ximp
five_imp2<-five2$ximp
five_imp3<-five3$ximp
five_imp4<-five4$ximp
five_imp5<-five5$ximp
```

#STEP 4# Pool Dataset

Step 3 created 5 different versions of data for each dataset.
Now we have to average those together to creat a single version of each of the 5 datasets
Then round the values to a single integer so they match standard ordinal paleopathology data

NOTE: that if this were imputing values for a real analysis, the results would be pooled at the very end according to Rubin's Rules

```{r}
five_one_imp <- as.data.frame((one_imp1 + one_imp2 + one_imp3 + one_imp4 + one_imp5)/5)
five_one_imp<-round(five_one_imp, digits=0)

five_two_imp <- as.data.frame((two_imp1 + two_imp2 + two_imp3 + two_imp4 + two_imp5)/5)
five_two_imp<-round(five_two_imp, digits=0)

five_three_imp <- as.data.frame((three_imp1 + three_imp2 + three_imp3 + three_imp4 + three_imp5)/5)
five_three_imp<-round(five_three_imp, digits=0)

five_four_imp <- as.data.frame((four_imp1 + four_imp2 + four_imp3 + four_imp4 + four_imp5)/5)
five_four_imp<-round(five_four_imp, digits=0)

five_five_imp <- as.data.frame((five_imp1 + five_imp2 + five_imp3 + five_imp4 + five_imp5)/5)
five_five_imp<-round(five_five_imp, digits=0)
```

#STEP 5# Calculate Success Parameters
Now that we have created 5 imputed datasets, we must assess how close the imputed values are to the original dataset

**Calculate Percent Error**

Here we establish the variable means for the complete dataset so we can calculate the percent error by variable at the end
```{r}
PHdatmean<-mean(data$PH)
COdatmean<-mean(data$CO)
PDdatmean<-mean(data$PD)
LEHdatmean<-mean(data$LEH)
periostosisdatmean<-mean(data$periostosis)
```

*Prepare Data to calculate Percent Error*
We must combine the means across each of the 5 versions by variable so that we produce a single percent error for each variable at the end. 
```{r}
PH.mean.imp<-mean(c(five_one_imp$PH, five_two_imp$PH, five_three_imp$PH, five_four_imp$PH, five_five_imp$PH))
CO.mean.imp<-mean(c(five_one_imp$CO, five_two_imp$CO, five_three_imp$CO, five_four_imp$CO, five_five_imp$CO))
PD.mean.imp<-mean(c(five_one_imp$PD, five_two_imp$PD, five_three_imp$PD, five_four_imp$PD, five_five_imp$PD))
LEH.mean.imp<-mean(c(five_one_imp$LEH, five_two_imp$LEH, five_three_imp$LEH, five_four_imp$LEH, five_five_imp$LEH))
periostosis.mean.imp<-mean(c(five_one_imp$periostosis, five_two_imp$periostosis, five_three_imp$periostosis, five_four_imp$periostosis, five_five_imp$periostosis))
```

Percent error is the absolute value of the observed value minus the expected value divided by the expected, all multiplied by 100
```{r}
ab<-c((abs((PH.mean.imp-PHdatmean)/PHdatmean)*100),(abs((CO.mean.imp-COdatmean)/COdatmean)*100),(abs((PD.mean.imp-PDdatmean)/PDdatmean)*100),(abs((LEH.mean.imp-LEHdatmean)/LEHdatmean)*100),(abs((periostosis.mean.imp-periostosisdatmean)/periostosisdatmean)*100))

write.csv(ab, file="PE.ord.rf.practice.csv")
```

**Calculate Normalized Root Mean Square Error (NRMSE)**

Both Practice.Ordinal.Dataset.csv and the 5 imputed datasets contain values that are 0s. However, NRMSE cannot be calculated when any of the values are 0. Therefore, we add 1 to every cell in the Practice.Ordinal.Dataset.csv and all the 5 imputed datasets. 
```{r}
data<-data+1
five_one_imp<-five_one_imp+1
five_two_imp<-five_two_imp+1
five_three_imp<-five_three_imp+1
five_four_imp<-five_four_imp+1
five_five_imp<-five_five_imp+1
```

Use hydroGOF package to assess NRMSE between observed and simulated values for each of the 5 versions of the imputed datasets

#five_one_imp
```{r}
obsA<-c(data$PH)
simA<-c(five_one_imp$PH)
dfA<-as.data.frame(t(gof(sim=simA, obs=obsA)))
A<-dfA$`NRMSE %`

obsB<-c(data$CO)
simB<-c(five_one_imp$CO)
dfB<-as.data.frame(t(gof(sim=simB, obs=obsB)))
B<-dfB$`NRMSE %`

obsC<-c(data$PD)
simC<-c(five_one_imp$PD)
dfC<-as.data.frame(t(gof(sim=simC, obs=obsC)))
C<-dfC$`NRMSE %`

obsD<-c(data$LEH)
simD<-c(five_one_imp$LEH)
dfD<-as.data.frame(t(gof(sim=simD, obs=obsD)))
D<-dfD$`NRMSE %`

obsE<-c(data$periostosis)
simE<-c(five_one_imp$periostosis)
dfE<-as.data.frame(t(gof(sim=simE, obs=obsE)))
E<-dfE$`NRMSE %`


```

#five_two_imp
```{r}
obsAA<-c(data$PH)
simAA<-c(five_two_imp$PH)
dfAA<-as.data.frame(t(gof(sim=simAA, obs=obsAA)))
AA<-dfAA$`NRMSE %`

obsBB<-c(data$CO)
simBB<-c(five_two_imp$CO)
dfBB<-as.data.frame(t(gof(sim=simBB, obs=obsBB)))
BB<-dfBB$`NRMSE %`

obsCC<-c(data$PD)
simCC<-c(five_two_imp$PD)
dfCC<-as.data.frame(t(gof(sim=simCC, obs=obsCC)))
CC<-dfCC$`NRMSE %`

obsDD<-c(data$LEH)
simDD<-c(five_two_imp$LEH)
dfDD<-as.data.frame(t(gof(sim=simDD, obs=obsDD)))
DD<-dfDD$`NRMSE %`

obsEE<-c(data$periostosis)
simEE<-c(five_two_imp$periostosis)
dfEE<-as.data.frame(t(gof(sim=simEE, obs=obsEE)))
EE<-dfEE$`NRMSE %`
```

#five_three_imp
```{r}
obsAAA<-c(data$PH)
simAAA<-c(five_three_imp$PH)
dfAAA<-as.data.frame(t(gof(sim=simAAA, obs=obsAAA)))
AAA<-dfAAA$`NRMSE %`

obsBBB<-c(data$CO)
simBBB<-c(five_three_imp$CO)
dfBBB<-as.data.frame(t(gof(sim=simBBB, obs=obsBBB)))
BBB<-dfBBB$`NRMSE %`

obsCCC<-c(data$PD)
simCCC<-c(five_three_imp$PD)
dfCCC<-as.data.frame(t(gof(sim=simCCC, obs=obsCCC)))
CCC<-dfCCC$`NRMSE %`

obsDDD<-c(data$LEH)
simDDD<-c(five_three_imp$LEH)
dfDDD<-as.data.frame(t(gof(sim=simDDD, obs=obsDDD)))
DDD<-dfDDD$`NRMSE %`

obsEEE<-c(data$periostosis)
simEEE<-c(five_three_imp$periostosis)
dfEEE<-as.data.frame(t(gof(sim=simEEE, obs=obsEEE)))
EEE<-dfEEE$`NRMSE %`
```

#five_four_imp
```{r}
obsAAAA<-c(data$PH)
simAAAA<-c(five_four_imp$PH)
dfAAAA<-as.data.frame(t(gof(sim=simAAAA, obs=obsAAAA)))
AAAA<-dfAAAA$`NRMSE %`

obsBBBB<-c(data$CO)
simBBBB<-c(five_four_imp$CO)
dfBBBB<-as.data.frame(t(gof(sim=simBBBB, obs=obsBBBB)))
BBBB<-dfBBBB$`NRMSE %`

obsCCCC<-c(data$PD)
simCCCC<-c(five_four_imp$PD)
dfCCCC<-as.data.frame(t(gof(sim=simCCCC, obs=obsCCCC)))
CCCC<-dfCCCC$`NRMSE %`

obsDDDD<-c(data$LEH)
simDDDD<-c(five_four_imp$LEH)
dfDDDD<-as.data.frame(t(gof(sim=simDDDD, obs=obsDDDD)))
DDDD<-dfDDDD$`NRMSE %`

obsEEEE<-c(data$periostosis)
simEEEE<-c(five_four_imp$periostosis)
dfEEEE<-as.data.frame(t(gof(sim=simEEEE, obs=obsEEEE)))
EEEE<-dfEEEE$`NRMSE %`

```

#five_five_imp
```{r}
obsAAAAA<-c(data$PH)
simAAAAA<-c(five_five_imp$PH)
dfAAAAA<-as.data.frame(t(gof(sim=simAAAAA, obs=obsAAAAA)))
AAAAA<-dfAAAAA$`NRMSE %`

obsBBBBB<-c(data$CO)
simBBBBB<-c(five_five_imp$CO)
dfBBBBB<-as.data.frame(t(gof(sim=simBBBBB, obs=obsBBBBB)))
BBBBB<-dfBBBBB$`NRMSE %`

obsCCCCC<-c(data$PD)
simCCCCC<-c(five_five_imp$PD)
dfCCCCC<-as.data.frame(t(gof(sim=simCCCCC, obs=obsCCCCC)))
CCCCC<-dfCCCCC$`NRMSE %`

obsDDDDD<-c(data$LEH)
simDDDDD<-c(five_five_imp$LEH)
dfDDDDD<-as.data.frame(t(gof(sim=simDDDDD, obs=obsDDDDD)))
DDDDD<-dfDDDDD$`NRMSE %`

obsEEEEE<-c(data$periostosis)
simEEEEE<-c(five_five_imp$periostosis)
dfEEEEE<-as.data.frame(t(gof(sim=simEEEEE, obs=obsEEEEE)))
EEEEE<-dfEEEEE$`NRMSE %`
```

Put each NRMSE into a matrix to create a usable dataframe that can be exported to Excel
```{r}
aa<-matrix(c(A, B, C, D, E), 1, 5)

ab<-matrix(c(AA, BB, CC, DD, EE), 1, 5)

ac<-matrix(c(AAA, BBB, CCC, DDD, EEE), 1, 5)

ad<-matrix(c(AAAA, BBBB, CCCC, DDDD, EEEE), 1, 5)

ae<-matrix(c(AAAAA, BBBBB, CCCCC, DDDDD, EEEEE), 1, 5)

df.ord.rf<-data.frame(rbind(aa, ab, ac, ad, ae))
colnames(df.ord.rf)<-c("PH", "CO", "PD", "LEH", "periostosis")
rownames(df.ord.rf)<-c("five_one_imp", "five_two_imp", "five_three_imp", "five_four_imp", "five_five_imp")
write.csv(df.ord.rf, file="nrmse.ordinal.rf.practice.csv")
```