####Expectation Maximization Imputation of Ordinal variables####

This example uses 5% missingness 

Packages Required: 
1) missMethods  https://cran.r-project.org/web/packages/missMethods/missMethods.pdf
2) hydroGOF  https://cran.r-project.org/web/packages/hydroGOF/hydroGOF.pdf

#STEP 1# Load packages and set working directory
```{r}
library(knitr)
rm(list=ls())

library(missMethods)
library(hydroGOF)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
```

#STEP 2# Load the data

*Practice.Continuous.Dataset.csv* is the complete dataset - i.e. no missing data. The complete dataset is needed in order to evaluate the success of the imputation/deletion method

*cont.five.1.practive.csv* is the first version of the complete dataset that has 5% of the values missing.
*cont.five.2.practice.csv* is the second version of the complete dataset that has 5% of the values missing. Etc. Each of the 5 versions has different values missing.

Having multiple versions ensures that the overall results are not due to random chance. Here, I chose 5 versions, but you could choose 3 or 10 or however many you want. 
```{r}
data<-read.csv("Practice.Ordinal.Dataset.csv", header=T)

ord.five.1<-read.csv("ord.five.1.practice.csv", header=T)
ord.five.2<-read.csv("ord.five.2.practice.csv", header=T)
ord.five.3<-read.csv("ord.five.3.practice.csv", header=T)
ord.five.4<-read.csv("ord.five.4.practice.csv", header=T)
ord.five.5<-read.csv("ord.five.5.practice.csv", header=T)
```

#STEP 3# Impute the Data

Use the impute_EM function from missMethods

We create 5 versions of each and average them together
Use the round function to round the values to the nearest integer to match paleopathology data

Dataset 1
```{r}
set.seed(1)
EMone1<-impute_EM(ord.five.1, stochastic=TRUE, verbose=TRUE)
EMone2<-impute_EM(ord.five.1, stochastic=TRUE, verbose=TRUE)
EMone3<-impute_EM(ord.five.1, stochastic=TRUE, verbose=TRUE)
EMone4<-impute_EM(ord.five.1, stochastic=TRUE, verbose=TRUE)
EMone5<-impute_EM(ord.five.1, stochastic=TRUE, verbose=TRUE)

EM_imp1<-(EMone1 + EMone2 + EMone3 + EMone4 + EMone5)/5
EM_imp1<-round(EM_imp1, digits=0)
```

Dataset 2
```{r}
set.seed(1)
EMtwo1<-impute_EM(ord.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo2<-impute_EM(ord.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo3<-impute_EM(ord.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo4<-impute_EM(ord.five.2, stochastic=TRUE, verbose=TRUE)
EMtwo5<-impute_EM(ord.five.2, stochastic=TRUE, verbose=TRUE)

EM_imp2<-(EMtwo1 + EMtwo2 + EMtwo3 + EMtwo4 + EMtwo5)/5
EM_imp2<-round(EM_imp2, digits=0)
```

Dataset 3
```{r}
set.seed(1)
EMthree1<-impute_EM(ord.five.3, stochastic=TRUE, verbose=TRUE)
EMthree2<-impute_EM(ord.five.3, stochastic=TRUE, verbose=TRUE)
EMthree3<-impute_EM(ord.five.3, stochastic=TRUE, verbose=TRUE)
EMthree4<-impute_EM(ord.five.3, stochastic=TRUE, verbose=TRUE)
EMthree5<-impute_EM(ord.five.3, stochastic=TRUE, verbose=TRUE)

EM_imp3<-(EMthree1 + EMthree2 + EMthree3 + EMthree4 + EMthree5)/5
EM_imp3<-round(EM_imp3, digits=0)
```

Dataset 4
```{r}
set.seed(1)
EMfour1<-impute_EM(ord.five.4, stochastic=TRUE, verbose=TRUE)
EMfour2<-impute_EM(ord.five.4, stochastic=TRUE, verbose=TRUE)
EMfour3<-impute_EM(ord.five.4, stochastic=TRUE, verbose=TRUE)
EMfour4<-impute_EM(ord.five.4, stochastic=TRUE, verbose=TRUE)
EMfour5<-impute_EM(ord.five.4, stochastic=TRUE, verbose=TRUE)

EM_imp4<-(EMfour1 + EMfour2 + EMfour3 + EMfour4 + EMfour5)/5
EM_imp4<-round(EM_imp4, digits=0)
```

Dataset 5
```{r}
set.seed(1)
EMfive1<-impute_EM(ord.five.5, stochastic=TRUE, verbose=TRUE)
EMfive2<-impute_EM(ord.five.5, stochastic=TRUE, verbose=TRUE)
EMfive3<-impute_EM(ord.five.5, stochastic=TRUE, verbose=TRUE)
EMfive4<-impute_EM(ord.five.5, stochastic=TRUE, verbose=TRUE)
EMfive5<-impute_EM(ord.five.5, stochastic=TRUE, verbose=TRUE)

EM_imp5<-(EMfive1 + EMfive2 + EMfive3 + EMfive4 + EMfive5)/5
EM_imp5<-round(EM_imp5, digits=0)
```


#STEP 5# Calculate Success Parameters
Now that we have created 5 imputed datasets, we must assess how close the imputed values are to the original dataset

**Calculate Percent Error**

Here we establish the variable means for the complete dataset so we can calculate the percent error by variable at the end
```{r}
PHdatmean<-mean(data$PH)
COdatmean<-mean(data$CO)
PDdatmean<-mean(data$PD)
LEHdatmean<-mean(data$LEH)
periostosisdatmean<-mean(data$periostosis)
```

*Prepare Data to calculate Percent Error*
We must combine the means across each of the 5 versions by variable so that we produce a single percent error for each variable at the end. 
```{r}
PH.mean.imp<-mean(c(EM_imp1$PH, EM_imp2$PH, EM_imp3$PH, EM_imp4$PH, EM_imp5$PH))
CO.mean.imp<-mean(c(EM_imp1$CO, EM_imp2$CO, EM_imp3$CO, EM_imp4$CO, EM_imp5$CO))
PD.mean.imp<-mean(c(EM_imp1$PD, EM_imp2$PD, EM_imp3$PD, EM_imp4$PD, EM_imp5$PD))
LEH.mean.imp<-mean(c(EM_imp1$LEH, EM_imp2$LEH, EM_imp3$LEH, EM_imp4$LEH, EM_imp5$LEH))
periostosis.mean.imp<-mean(c(EM_imp1$periostosis, EM_imp2$periostosis, EM_imp3$periostosis, EM_imp4$periostosis, EM_imp5$periostosis))
```

Percent error is the absolute value of the observed value minus the expected value divided by the expected, all multiplied by 100
```{r}
ab<-c((abs((PH.mean.imp-PHdatmean)/PHdatmean)*100),(abs((CO.mean.imp-COdatmean)/COdatmean)*100),(abs((PD.mean.imp-PDdatmean)/PDdatmean)*100),(abs((LEH.mean.imp-LEHdatmean)/LEHdatmean)*100),(abs((periostosis.mean.imp-periostosisdatmean)/periostosisdatmean)*100))

write.csv(ab, file="PE.ord.EM.practice.csv")
```


**Calculate Normalized Root Mean Square Error (NRMSE)**

Use hydroGOF package to assess NRMSE between observed and simulated values for each of the 5 versions of the imputed datasets

Both Practice.Ordinal.Dataset.csv and the 5 imputed datasets contain values that are 0s. However, NRMSE cannot be calculated when any of the values are 0. Therefore, we add 1 to every cell in the Practice.Ordinal.Dataset.csv and all the 5 imputed datasets. 
```{r}
data<-data+1
EM_imp1<-EM_imp1+1
EM_imp2<-EM_imp2+1
EM_imp3<-EM_imp3+1
EM_imp4<-EM_imp4+1
EM_imp5<-EM_imp5+1
```

Use hydroGOF package to assess NRMSE between observed and simulated values for each of the 5 versions of the imputed datasets

#EM_imp1
```{r}
obsA<-c(data$PH)
simA<-c(EM_imp1$PH)
dfA<-as.data.frame(t(gof(sim=simA, obs=obsA)))
A<-dfA$`NRMSE %`

obsB<-c(data$CO)
simB<-c(EM_imp1$CO)
dfB<-as.data.frame(t(gof(sim=simB, obs=obsB)))
B<-dfB$`NRMSE %`

obsC<-c(data$PD)
simC<-c(EM_imp1$PD)
dfC<-as.data.frame(t(gof(sim=simC, obs=obsC)))
C<-dfC$`NRMSE %`

obsD<-c(data$LEH)
simD<-c(EM_imp1$LEH)
dfD<-as.data.frame(t(gof(sim=simD, obs=obsD)))
D<-dfD$`NRMSE %`

obsE<-c(data$periostosis)
simE<-c(EM_imp1$periostosis)
dfE<-as.data.frame(t(gof(sim=simE, obs=obsE)))
E<-dfE$`NRMSE %`
```

#EM_imp2
```{r}
obsAA<-c(data$PH)
simAA<-c(EM_imp2$PH)
dfAA<-as.data.frame(t(gof(sim=simAA, obs=obsAA)))
AA<-dfAA$`NRMSE %`

obsBB<-c(data$CO)
simBB<-c(EM_imp2$CO)
dfBB<-as.data.frame(t(gof(sim=simBB, obs=obsBB)))
BB<-dfBB$`NRMSE %`

obsCC<-c(data$PD)
simCC<-c(EM_imp2$PD)
dfCC<-as.data.frame(t(gof(sim=simCC, obs=obsCC)))
CC<-dfCC$`NRMSE %`

obsDD<-c(data$LEH)
simDD<-c(EM_imp2$LEH)
dfDD<-as.data.frame(t(gof(sim=simDD, obs=obsDD)))
DD<-dfDD$`NRMSE %`

obsEE<-c(data$periostosis)
simEE<-c(EM_imp2$periostosis)
dfEE<-as.data.frame(t(gof(sim=simEE, obs=obsEE)))
EE<-dfEE$`NRMSE %`
```

#EM_imp3
```{r}
obsAAA<-c(data$PH)
simAAA<-c(EM_imp3$PH)
dfAAA<-as.data.frame(t(gof(sim=simAAA, obs=obsAAA)))
AAA<-dfAAA$`NRMSE %`

obsBBB<-c(data$CO)
simBBB<-c(EM_imp3$CO)
dfBBB<-as.data.frame(t(gof(sim=simBBB, obs=obsBBB)))
BBB<-dfBBB$`NRMSE %`

obsCCC<-c(data$PD)
simCCC<-c(EM_imp3$PD)
dfCCC<-as.data.frame(t(gof(sim=simCCC, obs=obsCCC)))
CCC<-dfCCC$`NRMSE %`

obsDDD<-c(data$LEH)
simDDD<-c(EM_imp3$LEH)
dfDDD<-as.data.frame(t(gof(sim=simDDD, obs=obsDDD)))
DDD<-dfDDD$`NRMSE %`

obsEEE<-c(data$periostosis)
simEEE<-c(EM_imp3$periostosis)
dfEEE<-as.data.frame(t(gof(sim=simEEE, obs=obsEEE)))
EEE<-dfEEE$`NRMSE %`
```

#EM_imp4
```{r}
obsAAAA<-c(data$PH)
simAAAA<-c(EM_imp4$PH)
dfAAAA<-as.data.frame(t(gof(sim=simAAAA, obs=obsAAAA)))
AAAA<-dfAAAA$`NRMSE %`

obsBBBB<-c(data$CO)
simBBBB<-c(EM_imp4$CO)
dfBBBB<-as.data.frame(t(gof(sim=simBBBB, obs=obsBBBB)))
BBBB<-dfBBBB$`NRMSE %`

obsCCCC<-c(data$PD)
simCCCC<-c(EM_imp4$PD)
dfCCCC<-as.data.frame(t(gof(sim=simCCCC, obs=obsCCCC)))
CCCC<-dfCCCC$`NRMSE %`

obsDDDD<-c(data$LEH)
simDDDD<-c(EM_imp4$LEH)
dfDDDD<-as.data.frame(t(gof(sim=simDDDD, obs=obsDDDD)))
DDDD<-dfDDDD$`NRMSE %`

obsEEEE<-c(data$periostosis)
simEEEE<-c(EM_imp4$periostosis)
dfEEEE<-as.data.frame(t(gof(sim=simEEEE, obs=obsEEEE)))
EEEE<-dfEEEE$`NRMSE %`
```

#EM_imp5
```{r}
obsAAAAA<-c(data$PH)
simAAAAA<-c(EM_imp5$PH)
dfAAAAA<-as.data.frame(t(gof(sim=simAAAAA, obs=obsAAAAA)))
AAAAA<-dfAAAAA$`NRMSE %`

obsBBBBB<-c(data$CO)
simBBBBB<-c(EM_imp5$CO)
dfBBBBB<-as.data.frame(t(gof(sim=simBBBBB, obs=obsBBBBB)))
BBBBB<-dfBBBBB$`NRMSE %`

obsCCCCC<-c(data$PD)
simCCCCC<-c(EM_imp5$PD)
dfCCCCC<-as.data.frame(t(gof(sim=simCCCCC, obs=obsCCCCC)))
CCCCC<-dfCCCCC$`NRMSE %`

obsDDDDD<-c(data$LEH)
simDDDDD<-c(EM_imp5$LEH)
dfDDDDD<-as.data.frame(t(gof(sim=simDDDDD, obs=obsDDDDD)))
DDDDD<-dfDDDDD$`NRMSE %`

obsEEEEE<-c(data$periostosis)
simEEEEE<-c(EM_imp5$periostosis)
dfEEEEE<-as.data.frame(t(gof(sim=simEEEEE, obs=obsEEEEE)))
EEEEE<-dfEEEEE$`NRMSE %`
```

Put each NRMSE into a matrix to create a usable dataframe that can be exported to Excel
```{r}
aa<-matrix(c(A, B, C, D, E), 1, 5)

ab<-matrix(c(AA, BB, CC, DD, EE), 1, 5)

ac<-matrix(c(AAA, BBB, CCC, DDD, EEE), 1, 5)

ad<-matrix(c(AAAA, BBBB, CCCC, DDDD, EEEE), 1, 5)

ae<-matrix(c(AAAAA, BBBBB, CCCCC, DDDDD, EEEEE), 1, 5)

df.ord.mean<-data.frame(rbind(aa, ab, ac, ad, ae))
colnames(df.ord.mean)<-c("PH", "CO", "PD", "LEH", "periostosis")
rownames(df.ord.mean)<-c("EM_imp1", "EM_imp2", "EM_imp3", "EM_imp4", "EM_imp5")
write.csv(df.ord.mean, file="nrmse.ordinal.EM.practice.csv")
```