#####Listwise Deletion of Ordinal variables#####

This example uses 5% missingness 
Packages Required: None

#STEP 1# Load packages and set working directory
```{r}
library(knitr)
rm(list=ls())

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
```

#STEP 2# Load the data

*Practice.Ordinal.Dataset.csv* is the complete dataset - i.e. no missing data. The complete dataset is needed in order to evaluate the success of the imputation/deletion method

*ord.five.1.practive.csv* is the first version of the complete dataset that has 5% of the values missing.
*ord.five.2.practice.csv* is the second version of the complete dataset that has 5% of the values missing. Etc. Each of the 5 versions has different values missing.

Having multiple versions ensures that the overall results are not due to random chance. Here, I chose 5 versions, but you could choose 3 or 10 or however many you want. 
```{r}
data<-read.csv("Practice.Ordinal.Dataset.csv", header=T)

ord.five.1<-read.csv("ord.five.1.practice.csv", header=T)
ord.five.2<-read.csv("ord.five.2.practice.csv", header=T)
ord.five.3<-read.csv("ord.five.3.practice.csv", header=T)
ord.five.4<-read.csv("ord.five.4.practice.csv", header=T)
ord.five.5<-read.csv("ord.five.5.practice.csv", header=T)
```


#STEP 3# Listwise Deletion
Use the "na.omit" function to remove all rows that have at least 1 NA
```{r}
ord.five.1<-na.omit(ord.five.1)
ord.five.2<-na.omit(ord.five.2)
ord.five.3<-na.omit(ord.five.3)
ord.five.4<-na.omit(ord.five.4)
ord.five.5<-na.omit(ord.five.5)
```


#STEP 4# Calculate Success Parameters

**Calculate Percent Error**

Now that we have created 5 imputed datasets, we must assess how close the imputed values are to the original dataset
Here we establish the variable means for the complete dataset so we can calculate the percent error by variable at the end
```{r}
PHdatmean<-mean(data$PH)
COdatmean<-mean(data$CO)
PDdatmean<-mean(data$PD)
LEHdatmean<-mean(data$LEH)
periostosisdatmean<-mean(data$periostosis)
```


**Prepare Data to calculate Percent Error**
We must combine the means across each of the 5 versions by variable so that we produce a single percent error for each variable at the end. 
```{r}
PH.mean.listwise<-mean(c(ord.five.1$PH, ord.five.2$PH, ord.five.3$PH, ord.five.4$PH, ord.five.5$PH))
CO.mean.listwise<-mean(c(ord.five.1$CO, ord.five.2$CO, ord.five.3$CO, ord.five.4$CO, ord.five.5$CO))
PD.mean.listwise<-mean(c(ord.five.1$PD, ord.five.2$PD, ord.five.3$PD, ord.five.4$PD, ord.five.5$PD))
LEH.mean.listwise<-mean(c(ord.five.1$LEH, ord.five.2$LEH, ord.five.3$LEH, ord.five.4$LEH, ord.five.5$LEH))
periostosis.mean.listwise<-mean(c(ord.five.1$periostosis, ord.five.2$periostosis, ord.five.3$periostosis, ord.five.4$periostosis, ord.five.5$periostosis))
```

**Calculate the Percent Error**

Percent error is the absolute value of the observed value minus the expected value divided by the expected, all multiplied by 100
```{r}
ab<-c((abs((PH.mean.listwise-PHdatmean)/PHdatmean)*100),(abs((CO.mean.listwise-COdatmean)/COdatmean)*100),(abs((PD.mean.listwise-PDdatmean)/PDdatmean)*100),(abs((LEH.mean.listwise-LEHdatmean)/LEHdatmean)*100),(abs((periostosis.mean.listwise-periostosisdatmean)/periostosisdatmean)*100))
```

Here we generate a dataframe that has the percent error for each variable and then export it as a .csv file
```{r}
df.listwise<-data.frame(ab)
colnames(df.listwise)<-c("PercentError")
rownames(df.listwise)<-c("PH", "CO", "PD", "LEH", "periostosis")
write.csv(df.listwise, file="Results.five.ordinal.listwise.practice.csv")
```
