####Stochastic Regression Imputation of Ordinal variables####

This example uses 5% missingness 

Packages Required: 
1) mice  https://cran.r-project.org/web/packages/mice/mice.pdf
2) hydroGOF  https://cran.r-project.org/web/packages/hydroGOF/hydroGOF.pdf

#STEP 1# Load packages and set working directory
```{r}
library(knitr)
rm(list=ls())

library(mice)
library(hydroGOF)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
```

#STEP 2# Load the data

*Practice.Ordinal.Dataset.csv* is the complete dataset - i.e. no missing data. The complete dataset is needed in order to evaluate the success of the imputation/deletion method

*ord.five.1.practive.csv* is the first version of the complete dataset that has 5% of the values missing.
*ord.five.2.practice.csv* is the second version of the complete dataset that has 5% of the values missing. Etc. Each of the 5 versions has different values missing.

Having multiple versions ensures that the overall results are not due to random chance. Here, I chose 5 versions, but you could choose 3 or 10 or however many you want. 
```{r}
data<-read.csv("Practice.Ordinal.Dataset.csv", header=T)

ord.five.1<-read.csv("ord.five.1.practice.csv", header=T)
ord.five.2<-read.csv("ord.five.2.practice.csv", header=T)
ord.five.3<-read.csv("ord.five.3.practice.csv", header=T)
ord.five.4<-read.csv("ord.five.4.practice.csv", header=T)
ord.five.5<-read.csv("ord.five.5.practice.csv", header=T)
```

#STEP 3# Impute the Data

#Impute the data using MICE package
*m=10* refers to how many different datasets we are going to create when we impute. *Multiple* imputation specifically calls for the creation of multiple imputed datasets to incorporate uncertainty of the imputed values. Usually you want to do at least 5-10. Each will have different imputed values
*maxit=50* refers to the number of iterations R will go through to create one of the M=3 datasets. I usually set it to maxit=50 but in the interest of speed we are doing 10
*method="norm.nob"* sets the code for regression imputation
*seed=1* is the starting number R will start at to run the iterations. If you don't set a seed # you will get a slightly different output each time. I picked 1 because that is in the range of what my data look like. 
*tempdata* = this is not the FINAL output so I name the output something temporary

```{r}
tempdata.five.1<-mice(ord.five.1, m=10, maxit=50, method="norm.nob", seed=1)
tempdata.five.2<-mice(ord.five.2, m=10, maxit=50, method="norm.nob", seed=1)
tempdata.five.3<-mice(ord.five.3, m=10, maxit=50, method="norm.nob", seed=1)
tempdata.five.4<-mice(ord.five.4, m=10, maxit=50, method="norm.nob", seed=1)
tempdata.five.5<-mice(ord.five.5, m=10, maxit=50, method="norm.nob", seed=1)
```

#STEP 4# Pool Dataset

Step 3 created 3 different versions of data for just the NAs.
Each of the m=10 versions of the dataset must now be pooled, creating 5 datasets that incorporate the variability in values. The "complete" function below inserts those imputed values in place of the NAs into the datasheet.
NOTE: that if this were imputing values for a real analysis, the results would be pooled at the very end according to Rubin's Rules

Pool Dataset 1
```{r}
one1<-complete(tempdata.five.1,1)
two1<-complete(tempdata.five.1,2)
three1<-complete(tempdata.five.1,3)
four1<-complete(tempdata.five.1,4)
five1<-complete(tempdata.five.1,5)  
six1<-complete(tempdata.five.1,6) 
seven1<-complete(tempdata.five.1,7) 
eight1<-complete(tempdata.five.1,8) 
nine1<-complete(tempdata.five.1,9) 
ten1<-complete(tempdata.five.1,10)

five_one_imp<-(one1 + two1 + three1 + four1 + five1 + six1 + seven1 + eight1 + nine1 + ten1)/10
five_one_imp<-round(five_one_imp, digits=0)
```

Pool Dataset 2
```{r}
one2<-complete(tempdata.five.2,1)
two2<-complete(tempdata.five.2,2)
three2<-complete(tempdata.five.2,3)
four2<-complete(tempdata.five.2,4)
five2<-complete(tempdata.five.2,5)
six2<-complete(tempdata.five.2,6) 
seven2<-complete(tempdata.five.2,7) 
eight2<-complete(tempdata.five.2,8) 
nine2<-complete(tempdata.five.2,9) 
ten2<-complete(tempdata.five.2,10)

five_two_imp<-(one2 + two2 + three2 + four2 + five2 + six2 + seven2 + eight2 + nine2 + ten2)/10
five_two_imp<-round(five_two_imp, digits=0)
```

Pool Dataset 3
```{r}
one3<-complete(tempdata.five.3,1)
two3<-complete(tempdata.five.3,2)
three3<-complete(tempdata.five.3,3)
four3<-complete(tempdata.five.3,4)
five3<-complete(tempdata.five.3,5)  
six3<-complete(tempdata.five.3,6) 
seven3<-complete(tempdata.five.3,7) 
eight3<-complete(tempdata.five.3,8) 
nine3<-complete(tempdata.five.3,9) 
ten3<-complete(tempdata.five.3,10)

five_three_imp<-(one3 + two3 + three3 + four3 + five3 + six3 + seven3 + eight3 + nine3 + ten3)/10
five_three_imp<-round(five_three_imp, digits=0)
```

Pool Dataset 4
```{r}
one4<-complete(tempdata.five.4,1)
two4<-complete(tempdata.five.4,2)
three4<-complete(tempdata.five.4,3)
four4<-complete(tempdata.five.4,4)
five4<-complete(tempdata.five.4,5)  
six4<-complete(tempdata.five.4,6) 
seven4<-complete(tempdata.five.4,7) 
eight4<-complete(tempdata.five.4,8) 
nine4<-complete(tempdata.five.4,9) 
ten4<-complete(tempdata.five.4,10)

five_four_imp<-(one4 + two4 + three4 + four4 + five4 + six4 + seven4 + eight4 + nine4 + ten4)/10
five_four_imp<-round(five_four_imp, digits=0)
```

Pool Dataset 5
```{r}
one5<-complete(tempdata.five.5,1)
two5<-complete(tempdata.five.5,2)
three5<-complete(tempdata.five.5,3)
four5<-complete(tempdata.five.5,4)
five5<-complete(tempdata.five.5,5) 
six5<-complete(tempdata.five.5,6) 
seven5<-complete(tempdata.five.5,7) 
eight5<-complete(tempdata.five.5,8) 
nine5<-complete(tempdata.five.5,9) 
ten5<-complete(tempdata.five.5,10)

five_five_imp<-(one5 + two5 + three5 + four5 + five5 + six5 + seven5 + eight5 + nine5 + ten5)/10
five_five_imp<-round(five_five_imp, digits=0)
```

#STEP 5# Calculate Success Parameters
Now that we have created 5 imputed datasets, we must assess how close the imputed values are to the original dataset

**Calculate Percent Error**

Here we establish the variable means for the complete dataset so we can calculate the percent error by variable at the end
```{r}
PHdatmean<-mean(data$PH)
COdatmean<-mean(data$CO)
PDdatmean<-mean(data$PD)
LEHdatmean<-mean(data$LEH)
periostosisdatmean<-mean(data$periostosis)
```

*Prepare Data to calculate Percent Error*
We must combine the means across each of the 5 versions by variable so that we produce a single percent error for each variable at the end. 
```{r}
PH.mean.imp<-mean(c(five_one_imp$PH, five_two_imp$PH, five_three_imp$PH, five_four_imp$PH, five_five_imp$PH))
CO.mean.imp<-mean(c(five_one_imp$CO, five_two_imp$CO, five_three_imp$CO, five_four_imp$CO, five_five_imp$CO))
PD.mean.imp<-mean(c(five_one_imp$PD, five_two_imp$PD, five_three_imp$PD, five_four_imp$PD, five_five_imp$PD))
LEH.mean.imp<-mean(c(five_one_imp$LEH, five_two_imp$LEH, five_three_imp$LEH, five_four_imp$LEH, five_five_imp$LEH))
periostosis.mean.imp<-mean(c(five_one_imp$periostosis, five_two_imp$periostosis, five_three_imp$periostosis, five_four_imp$periostosis, five_five_imp$periostosis))
```

Percent error is the absolute value of the observed value minus the expected value divided by the expected, all multiplied by 100
```{r}
ab<-c((abs((PH.mean.imp-PHdatmean)/PHdatmean)*100),(abs((CO.mean.imp-COdatmean)/COdatmean)*100),(abs((PD.mean.imp-PDdatmean)/PDdatmean)*100),(abs((LEH.mean.imp-LEHdatmean)/LEHdatmean)*100),(abs((periostosis.mean.imp-periostosisdatmean)/periostosisdatmean)*100))

write.csv(ab, file="PE.ord.reg.practice.csv")
```


**Calculate Normalized Root Mean Square Error (NRMSE)**

Both Practice.Ordinal.Dataset.csv and the 5 imputed datasets contain values that are 0s. However, NRMSE cannot be calculated when any of the values are 0. Therefore, we add 1 to every cell in the Practice.Ordinal.Dataset.csv and all the 5 imputed datasets. 
```{r}
data<-data+1
five_one_imp<-five_one_imp+1
five_two_imp<-five_two_imp+1
five_three_imp<-five_three_imp+1
five_four_imp<-five_four_imp+1
five_five_imp<-five_five_imp+1
```

Use hydroGOF package to assess NRMSE between observed and simulated values for each of the 5 versions of the imputed datasets

#five_one_imp
```{r}
obsA<-c(data$PH)
simA<-c(five_one_imp$PH)
dfA<-as.data.frame(t(gof(sim=simA, obs=obsA)))
A<-dfA$`NRMSE %`

obsB<-c(data$CO)
simB<-c(five_one_imp$CO)
dfB<-as.data.frame(t(gof(sim=simB, obs=obsB)))
B<-dfB$`NRMSE %`

obsC<-c(data$PD)
simC<-c(five_one_imp$PD)
dfC<-as.data.frame(t(gof(sim=simC, obs=obsC)))
C<-dfC$`NRMSE %`

obsD<-c(data$LEH)
simD<-c(five_one_imp$LEH)
dfD<-as.data.frame(t(gof(sim=simD, obs=obsD)))
D<-dfD$`NRMSE %`

obsE<-c(data$periostosis)
simE<-c(five_one_imp$periostosis)
dfE<-as.data.frame(t(gof(sim=simE, obs=obsE)))
E<-dfE$`NRMSE %`


```

#five_two_imp
```{r}
obsAA<-c(data$PH)
simAA<-c(five_two_imp$PH)
dfAA<-as.data.frame(t(gof(sim=simAA, obs=obsAA)))
AA<-dfAA$`NRMSE %`

obsBB<-c(data$CO)
simBB<-c(five_two_imp$CO)
dfBB<-as.data.frame(t(gof(sim=simBB, obs=obsBB)))
BB<-dfBB$`NRMSE %`

obsCC<-c(data$PD)
simCC<-c(five_two_imp$PD)
dfCC<-as.data.frame(t(gof(sim=simCC, obs=obsCC)))
CC<-dfCC$`NRMSE %`

obsDD<-c(data$LEH)
simDD<-c(five_two_imp$LEH)
dfDD<-as.data.frame(t(gof(sim=simDD, obs=obsDD)))
DD<-dfDD$`NRMSE %`

obsEE<-c(data$periostosis)
simEE<-c(five_two_imp$periostosis)
dfEE<-as.data.frame(t(gof(sim=simEE, obs=obsEE)))
EE<-dfEE$`NRMSE %`
```

#five_three_imp
```{r}
obsAAA<-c(data$PH)
simAAA<-c(five_three_imp$PH)
dfAAA<-as.data.frame(t(gof(sim=simAAA, obs=obsAAA)))
AAA<-dfAAA$`NRMSE %`

obsBBB<-c(data$CO)
simBBB<-c(five_three_imp$CO)
dfBBB<-as.data.frame(t(gof(sim=simBBB, obs=obsBBB)))
BBB<-dfBBB$`NRMSE %`

obsCCC<-c(data$PD)
simCCC<-c(five_three_imp$PD)
dfCCC<-as.data.frame(t(gof(sim=simCCC, obs=obsCCC)))
CCC<-dfCCC$`NRMSE %`

obsDDD<-c(data$LEH)
simDDD<-c(five_three_imp$LEH)
dfDDD<-as.data.frame(t(gof(sim=simDDD, obs=obsDDD)))
DDD<-dfDDD$`NRMSE %`

obsEEE<-c(data$periostosis)
simEEE<-c(five_three_imp$periostosis)
dfEEE<-as.data.frame(t(gof(sim=simEEE, obs=obsEEE)))
EEE<-dfEEE$`NRMSE %`
```

#five_four_imp
```{r}
obsAAAA<-c(data$PH)
simAAAA<-c(five_four_imp$PH)
dfAAAA<-as.data.frame(t(gof(sim=simAAAA, obs=obsAAAA)))
AAAA<-dfAAAA$`NRMSE %`

obsBBBB<-c(data$CO)
simBBBB<-c(five_four_imp$CO)
dfBBBB<-as.data.frame(t(gof(sim=simBBBB, obs=obsBBBB)))
BBBB<-dfBBBB$`NRMSE %`

obsCCCC<-c(data$PD)
simCCCC<-c(five_four_imp$PD)
dfCCCC<-as.data.frame(t(gof(sim=simCCCC, obs=obsCCCC)))
CCCC<-dfCCCC$`NRMSE %`

obsDDDD<-c(data$LEH)
simDDDD<-c(five_four_imp$LEH)
dfDDDD<-as.data.frame(t(gof(sim=simDDDD, obs=obsDDDD)))
DDDD<-dfDDDD$`NRMSE %`

obsEEEE<-c(data$periostosis)
simEEEE<-c(five_four_imp$periostosis)
dfEEEE<-as.data.frame(t(gof(sim=simEEEE, obs=obsEEEE)))
EEEE<-dfEEEE$`NRMSE %`

```

#five_five_imp
```{r}
obsAAAAA<-c(data$PH)
simAAAAA<-c(five_five_imp$PH)
dfAAAAA<-as.data.frame(t(gof(sim=simAAAAA, obs=obsAAAAA)))
AAAAA<-dfAAAAA$`NRMSE %`

obsBBBBB<-c(data$CO)
simBBBBB<-c(five_five_imp$CO)
dfBBBBB<-as.data.frame(t(gof(sim=simBBBBB, obs=obsBBBBB)))
BBBBB<-dfBBBBB$`NRMSE %`

obsCCCCC<-c(data$PD)
simCCCCC<-c(five_five_imp$PD)
dfCCCCC<-as.data.frame(t(gof(sim=simCCCCC, obs=obsCCCCC)))
CCCCC<-dfCCCCC$`NRMSE %`

obsDDDDD<-c(data$LEH)
simDDDDD<-c(five_five_imp$LEH)
dfDDDDD<-as.data.frame(t(gof(sim=simDDDDD, obs=obsDDDDD)))
DDDDD<-dfDDDDD$`NRMSE %`

obsEEEEE<-c(data$periostosis)
simEEEEE<-c(five_five_imp$periostosis)
dfEEEEE<-as.data.frame(t(gof(sim=simEEEEE, obs=obsEEEEE)))
EEEEE<-dfEEEEE$`NRMSE %`
```

Put each NRMSE into a matrix to create a usable dataframe that can be exported to Excel
```{r}
aa<-matrix(c(A, B, C, D, E), 1, 5)

ab<-matrix(c(AA, BB, CC, DD, EE), 1, 5)

ac<-matrix(c(AAA, BBB, CCC, DDD, EEE), 1, 5)

ad<-matrix(c(AAAA, BBBB, CCCC, DDDD, EEEE), 1, 5)

ae<-matrix(c(AAAAA, BBBBB, CCCCC, DDDDD, EEEEE), 1, 5)

df.ord.mean<-data.frame(rbind(aa, ab, ac, ad, ae))
colnames(df.ord.mean)<-c("PH", "CO", "PD", "LEH", "periostosis")
rownames(df.ord.mean)<-c("five_one_imp", "five_two_imp", "five_three_imp", "five_four_imp", "five_five_imp")
write.csv(df.ord.mean, file="nrmse.ordinal.reg.practice.csv")
```