####Random Forest Imputation of continuous variables####

This example uses 5% missingness 

Packages Required: 
1) missMethods  https://cran.r-project.org/web/packages/missMethods/missMethods.pdf
2) hydroGOF  https://cran.r-project.org/web/packages/hydroGOF/hydroGOF.pdf

#STEP 1# Load packages and set working directory
```{r}
library(knitr)
rm(list=ls())

library(missForest)
library(hydroGOF)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
```

#STEP 2# Load the data

*Practice.Continuous.Dataset.csv* is the complete dataset - i.e. no missing data. The complete dataset is needed in conter to evaluate the success of the imputation/deletion method

*cont.five.1.practive.csv* is the first version of the complete dataset that has 5% of the values missing.
*cont.five.2.practice.csv* is the second version of the complete dataset that has 5% of the values missing. Etc. Each of the 5 versions has different values missing.

Having multiple versions ensures that the overall results are not due to random chance. Here, I chose 5 versions, but you could choose 3 or 10 or however many you want. 
```{r}
data<-read.csv("Practice.Continuous.Dataset.csv", header=T)

cont.five.1<-read.csv("cont.five.1.practice.csv", header=T)
cont.five.2<-read.csv("cont.five.2.practice.csv", header=T)
cont.five.3<-read.csv("cont.five.3.practice.csv", header=T)
cont.five.4<-read.csv("cont.five.4.practice.csv", header=T)
cont.five.5<-read.csv("cont.five.5.practice.csv", header=T)
```

#STEP 3# Impute the Data

#Impute the data using missForest package
*maxiter=10* refers to the maximum number of iterations to be performed
*ntree=200* refers to the number of trees to grow
*verbose=FALSE"* if TRUE more information is produced between each iteration
*replace=TRUE* If 'TRUE' bootstrap sampling (with replacements) is performed
*one1* = this is not the FINAL output so I name the output something temporary

```{r}
set.seed(0)
one1<-missForest(cont.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one2<-missForest(cont.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one3<-missForest(cont.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one4<-missForest(cont.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
one5<-missForest(cont.five.1, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(1)
two1<-missForest(cont.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two2<-missForest(cont.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two3<-missForest(cont.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two4<-missForest(cont.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
two5<-missForest(cont.five.2, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(2)
three1<-missForest(cont.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three2<-missForest(cont.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three3<-missForest(cont.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three4<-missForest(cont.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
three5<-missForest(cont.five.3, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(3)
four1<-missForest(cont.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four2<-missForest(cont.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four3<-missForest(cont.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four4<-missForest(cont.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
four5<-missForest(cont.five.4, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)

set.seed(4)
five1<-missForest(cont.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five2<-missForest(cont.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five3<-missForest(cont.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five4<-missForest(cont.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
five5<-missForest(cont.five.5, maxiter=10, ntree=200, verbose= FALSE, replace=TRUE)
```

Extract the completed dataframes from the list
```{r}
one_imp1<-one1$ximp
one_imp2<-one2$ximp
one_imp3<-one3$ximp
one_imp4<-one4$ximp
one_imp5<-one5$ximp

two_imp1<-two1$ximp
two_imp2<-two2$ximp
two_imp3<-two3$ximp
two_imp4<-two4$ximp
two_imp5<-two5$ximp

three_imp1<-three1$ximp
three_imp2<-three2$ximp
three_imp3<-three3$ximp
three_imp4<-three4$ximp
three_imp5<-three5$ximp

four_imp1<-four1$ximp
four_imp2<-four2$ximp
four_imp3<-four3$ximp
four_imp4<-four4$ximp
four_imp5<-four5$ximp

five_imp1<-five1$ximp
five_imp2<-five2$ximp
five_imp3<-five3$ximp
five_imp4<-five4$ximp
five_imp5<-five5$ximp
```

#STEP 4# Pool Dataset

Step 3 created 5 different versions of data for each dataset.
Now we have to average those together to creat a single version of each of the 5 datasets

NOTE: that if this were imputing values for a real analysis, the results would be pooled at the very end according to Rubin's Rules

```{r}
five_one_imp <- as.data.frame((one_imp1 + one_imp2 + one_imp3 + one_imp4 + one_imp5)/5)

five_two_imp <- as.data.frame((two_imp1 + two_imp2 + two_imp3 + two_imp4 + two_imp5)/5)

five_three_imp <- as.data.frame((three_imp1 + three_imp2 + three_imp3 + three_imp4 + three_imp5)/5)

five_four_imp <- as.data.frame((four_imp1 + four_imp2 + four_imp3 + four_imp4 + four_imp5)/5)

five_five_imp <- as.data.frame((five_imp1 + five_imp2 + five_imp3 + five_imp4 + five_imp5)/5)
```

#STEP 5# Calculate Success Parameters
Now that we have created 5 imputed datasets, we must assess how close the imputed values are to the original dataset

**Calculate Percent Error**

Here we establish the variable means for the complete dataset so we can calculate the percent error by variable at the end
```{r}
FL.Ldatmean<-mean(data$FL.Left)
FL.Rdatmean<-mean(data$FL.Right)
T1.APdatmean<-mean(data$T1.AP)
T1.TRdatmean<-mean(data$T1.TR)
T5.APdatmean<-mean(data$T5.AP)
T5.TRdatmean<-mean(data$T5.TR)
T10.APdatmean<-mean(data$T10.AP)
T10.TRdatmean<-mean(data$T10.TR)
L1.APdatmean<-mean(data$L1.AP)
L1.TRdatmean<-mean(data$L1.TR)
L3.APdatmean<-mean(data$L3.AP)
L3.TRdatmean<-mean(data$L3.TR)
```


*Prepare Data to calculate Percent Error*
We must combine the means across each of the 5 versions by variable so that we produce a single percent error for each variable at the end. 
```{r}
FL.L.mean.imp<-mean(c(five_one_imp$FL.Left, five_two_imp$FL.Left, five_three_imp$FL.Left, five_four_imp$FL.Left, five_five_imp$FL.Left))
FL.R.mean.imp<-mean(c(five_one_imp$FL.Right, five_two_imp$FL.Right, five_three_imp$FL.Right, five_four_imp$FL.Right, five_five_imp$FL.Right))
T1.AP.mean.imp<-mean(c(five_one_imp$T1.AP, five_two_imp$T1.AP, five_three_imp$T1.AP, five_four_imp$T1.AP, five_five_imp$T1.AP))
T1.TR.mean.imp<-mean(c(five_one_imp$T1.TR, five_two_imp$T1.TR, five_three_imp$T1.TR, five_four_imp$T1.TR, five_five_imp$T1.TR))
T5.AP.mean.imp<-mean(c(five_one_imp$T5.AP, five_two_imp$T5.AP, five_three_imp$T5.AP, five_four_imp$T5.AP, five_five_imp$T5.AP))
T5.TR.mean.imp<-mean(c(five_one_imp$T5.TR, five_two_imp$T5.TR, five_three_imp$T5.TR, five_four_imp$T5.TR, five_five_imp$T5.TR))
T10.AP.mean.imp<-mean(c(five_one_imp$T10.AP, five_two_imp$T10.AP, five_three_imp$T10.AP, five_four_imp$T10.AP, five_five_imp$T10.AP))
T10.TR.mean.imp<-mean(c(five_one_imp$T10.TR, five_two_imp$T10.TR, five_three_imp$T10.TR, five_four_imp$T10.TR, five_five_imp$T10.TR))
L1.AP.mean.imp<-mean(c(five_one_imp$L1.AP, five_two_imp$L1.AP, five_three_imp$L1.AP, five_four_imp$L1.AP, five_five_imp$L1.AP))
L1.TR.mean.imp<-mean(c(five_one_imp$L1.TR, five_two_imp$L1.TR, five_three_imp$L1.TR, five_four_imp$L1.TR, five_five_imp$L1.TR))
L3.AP.mean.imp<-mean(c(five_one_imp$L3.AP, five_two_imp$L3.AP, five_three_imp$L3.AP, five_four_imp$L3.AP, five_five_imp$L3.AP))
L3.TR.mean.imp<-mean(c(five_one_imp$L3.TR, five_two_imp$L3.TR, five_three_imp$L3.TR, five_four_imp$L3.TR, five_five_imp$L3.TR))
```

Percent error is the absolute value of the observed value minus the expected value divided by the expected, all multiplied by 100
```{r}
ab<-c((abs((FL.L.mean.imp-FL.Ldatmean)/FL.Ldatmean)*100),(abs((FL.R.mean.imp-FL.Rdatmean)/FL.Rdatmean)*100),(abs((T1.AP.mean.imp-T1.APdatmean)/T1.APdatmean)*100),(abs((T1.TR.mean.imp-T1.TRdatmean)/T1.TRdatmean)*100),(abs((T5.AP.mean.imp-T5.APdatmean)/T5.APdatmean)*100), (abs((T5.TR.mean.imp-T5.TRdatmean)/T5.TRdatmean)*100), (abs((T10.AP.mean.imp-T10.APdatmean)/T10.APdatmean)*100), (abs((T10.TR.mean.imp-T10.TRdatmean)/T10.TRdatmean)*100), (abs((L1.AP.mean.imp-L1.APdatmean)/L1.APdatmean)*100), (abs((L1.TR.mean.imp-L1.TRdatmean)/L1.TRdatmean)*100), (abs((L3.AP.mean.imp-L3.APdatmean)/L3.APdatmean)*100), (abs((L3.TR.mean.imp-L3.TRdatmean)/L3.TRdatmean)*100))

write.csv(ab, file="PE.cont.rf.csv")
```


**Calculate Normalized Root Mean Square Error (NRMSE)**

Use hydroGOF package to assess NRMSE between observed and simulated values for each of the 5 versions of the imputed datasets

#five_one_imp
```{r}
obsA<-c(data$FL.Left)
simA<-c(five_one_imp$FL.Left)
dfA<-as.data.frame(t(gof(sim=simA, obs=obsA)))
A<-dfA$`NRMSE %`

obsB<-c(data$FL.Right)
simB<-c(five_one_imp$FL.Right)
dfB<-as.data.frame(t(gof(sim=simB, obs=obsB)))
B<-dfB$`NRMSE %`

obsC<-c(data$T1.AP)
simC<-c(five_one_imp$T1.AP)
dfC<-as.data.frame(t(gof(sim=simC, obs=obsC)))
C<-dfC$`NRMSE %`

obsD<-c(data$T1.TR)
simD<-c(five_one_imp$T1.TR)
dfD<-as.data.frame(t(gof(sim=simD, obs=obsD)))
D<-dfD$`NRMSE %`

obsE<-c(data$T5.AP)
simE<-c(five_one_imp$T5.AP)
dfE<-as.data.frame(t(gof(sim=simE, obs=obsE)))
E<-dfE$`NRMSE %`

obsF<-c(data$T5.TR)
simF<-c(five_one_imp$T5.TR)
dfF<-as.data.frame(t(gof(sim=simF, obs=obsF)))
F<-dfF$`NRMSE %`

obsG<-c(data$T10.AP)
simG<-c(five_one_imp$T10.AP)
dfG<-as.data.frame(t(gof(sim=simG, obs=obsG)))
G<-dfG$`NRMSE %`

obsH<-c(data$T10.TR)
simH<-c(five_one_imp$T10.TR)
dfH<-as.data.frame(t(gof(sim=simH, obs=obsH)))
H<-dfH$`NRMSE %`

obsI<-c(data$L1.AP)
simI<-c(five_one_imp$L1.AP)
dfI<-as.data.frame(t(gof(sim=simI, obs=obsI)))
I<-dfI$`NRMSE %`

obsJ<-c(data$L1.TR)
simJ<-c(five_one_imp$L1.TR)
dfJ<-as.data.frame(t(gof(sim=simJ, obs=obsJ)))
J<-dfJ$`NRMSE %`

obsK<-c(data$L3.AP)
simK<-c(five_one_imp$L3.AP)
dfK<-as.data.frame(t(gof(sim=simK, obs=obsK)))
K<-dfK$`NRMSE %`

obsL<-c(data$L3.TR)
simL<-c(five_one_imp$L3.TR)
dfL<-as.data.frame(t(gof(sim=simL, obs=obsL)))
L<-dfL$`NRMSE %`
```

#five_two_imp
```{r}
obsAA<-c(data$FL.Left)
simAA<-c(five_two_imp$FL.Left)
dfAA<-as.data.frame(t(gof(sim=simAA, obs=obsAA)))
AA<-dfAA$`NRMSE %`

obsBB<-c(data$FL.Right)
simBB<-c(five_two_imp$FL.Right)
dfBB<-as.data.frame(t(gof(sim=simBB, obs=obsBB)))
BB<-dfBB$`NRMSE %`

obsCC<-c(data$T1.AP)
simCC<-c(five_two_imp$T1.AP)
dfCC<-as.data.frame(t(gof(sim=simCC, obs=obsCC)))
CC<-dfCC$`NRMSE %`

obsDD<-c(data$T1.TR)
simDD<-c(five_two_imp$T1.TR)
dfDD<-as.data.frame(t(gof(sim=simDD, obs=obsDD)))
DD<-dfDD$`NRMSE %`

obsEE<-c(data$T5.AP)
simEE<-c(five_two_imp$T5.AP)
dfEE<-as.data.frame(t(gof(sim=simEE, obs=obsEE)))
EE<-dfEE$`NRMSE %`

obsFF<-c(data$T5.TR)
simFF<-c(five_two_imp$T5.TR)
dfFF<-as.data.frame(t(gof(sim=simFF, obs=obsFF)))
FF<-dfFF$`NRMSE %`

obsGG<-c(data$T10.AP)
simGG<-c(five_two_imp$T10.AP)
dfGG<-as.data.frame(t(gof(sim=simGG, obs=obsGG)))
GG<-dfGG$`NRMSE %`

obsHH<-c(data$T10.TR)
simHH<-c(five_two_imp$T10.TR)
dfHH<-as.data.frame(t(gof(sim=simHH, obs=obsHH)))
HH<-dfHH$`NRMSE %`

obsII<-c(data$L1.AP)
simII<-c(five_two_imp$L1.AP)
dfII<-as.data.frame(t(gof(sim=simII, obs=obsII)))
II<-dfII$`NRMSE %`

obsJJ<-c(data$L1.TR)
simJJ<-c(five_two_imp$L1.TR)
dfJJ<-as.data.frame(t(gof(sim=simJJ, obs=obsJJ)))
JJ<-dfJJ$`NRMSE %`

obsKK<-c(data$L3.AP)
simKK<-c(five_two_imp$L3.AP)
dfKK<-as.data.frame(t(gof(sim=simKK, obs=obsKK)))
KK<-dfKK$`NRMSE %`

obsLL<-c(data$L3.TR)
simLL<-c(five_two_imp$L3.TR)
dfLL<-as.data.frame(t(gof(sim=simLL, obs=obsLL)))
LL<-dfLL$`NRMSE %`
```

#five_three_imp
```{r}
obsAAA<-c(data$FL.Left)
simAAA<-c(five_three_imp$FL.Left)
dfAAA<-as.data.frame(t(gof(sim=simAAA, obs=obsAAA)))
AAA<-dfAAA$`NRMSE %`

obsBBB<-c(data$FL.Right)
simBBB<-c(five_three_imp$FL.Right)
dfBBB<-as.data.frame(t(gof(sim=simBBB, obs=obsBBB)))
BBB<-dfBBB$`NRMSE %`

obsCCC<-c(data$T1.AP)
simCCC<-c(five_three_imp$T1.AP)
dfCCC<-as.data.frame(t(gof(sim=simCCC, obs=obsCCC)))
CCC<-dfCCC$`NRMSE %`

obsDDD<-c(data$T1.TR)
simDDD<-c(five_three_imp$T1.TR)
dfDDD<-as.data.frame(t(gof(sim=simDDD, obs=obsDDD)))
DDD<-dfDDD$`NRMSE %`

obsEEE<-c(data$T5.AP)
simEEE<-c(five_three_imp$T5.AP)
dfEEE<-as.data.frame(t(gof(sim=simEEE, obs=obsEEE)))
EEE<-dfEEE$`NRMSE %`

obsFFF<-c(data$T5.TR)
simFFF<-c(five_three_imp$T5.TR)
dfFFF<-as.data.frame(t(gof(sim=simFFF, obs=obsFFF)))
FFF<-dfFFF$`NRMSE %`

obsGGG<-c(data$T10.AP)
simGGG<-c(five_three_imp$T10.AP)
dfGGG<-as.data.frame(t(gof(sim=simGGG, obs=obsGGG)))
GGG<-dfGGG$`NRMSE %`

obsHHH<-c(data$T10.TR)
simHHH<-c(five_three_imp$T10.TR)
dfHHH<-as.data.frame(t(gof(sim=simHHH, obs=obsHHH)))
HHH<-dfHHH$`NRMSE %`

obsIII<-c(data$L1.AP)
simIII<-c(five_three_imp$L1.AP)
dfIII<-as.data.frame(t(gof(sim=simIII, obs=obsIII)))
III<-dfIII$`NRMSE %`

obsJJJ<-c(data$L1.TR)
simJJJ<-c(five_three_imp$L1.TR)
dfJJJ<-as.data.frame(t(gof(sim=simJJJ, obs=obsJJJ)))
JJJ<-dfJJJ$`NRMSE %`

obsKKK<-c(data$L3.AP)
simKKK<-c(five_three_imp$L3.AP)
dfKKK<-as.data.frame(t(gof(sim=simKKK, obs=obsKKK)))
KKK<-dfKKK$`NRMSE %`

obsLLL<-c(data$L3.TR)
simLLL<-c(five_three_imp$L3.TR)
dfLLL<-as.data.frame(t(gof(sim=simLLL, obs=obsLLL)))
LLL<-dfLLL$`NRMSE %`
```

#five_four_imp
```{r}
obsAAAA<-c(data$FL.Left)
simAAAA<-c(five_four_imp$FL.Left)
dfAAAA<-as.data.frame(t(gof(sim=simAAAA, obs=obsAAAA)))
AAAA<-dfAAAA$`NRMSE %`

obsBBBB<-c(data$FL.Right)
simBBBB<-c(five_four_imp$FL.Right)
dfBBBB<-as.data.frame(t(gof(sim=simBBBB, obs=obsBBBB)))
BBBB<-dfBBBB$`NRMSE %`

obsCCCC<-c(data$T1.AP)
simCCCC<-c(five_four_imp$T1.AP)
dfCCCC<-as.data.frame(t(gof(sim=simCCCC, obs=obsCCCC)))
CCCC<-dfCCCC$`NRMSE %`

obsDDDD<-c(data$T1.TR)
simDDDD<-c(five_four_imp$T1.TR)
dfDDDD<-as.data.frame(t(gof(sim=simDDDD, obs=obsDDDD)))
DDDD<-dfDDDD$`NRMSE %`

obsEEEE<-c(data$T5.AP)
simEEEE<-c(five_four_imp$T5.AP)
dfEEEE<-as.data.frame(t(gof(sim=simEEEE, obs=obsEEEE)))
EEEE<-dfEEEE$`NRMSE %`

obsFFFF<-c(data$T5.TR)
simFFFF<-c(five_four_imp$T5.TR)
dfFFFF<-as.data.frame(t(gof(sim=simFFFF, obs=obsFFFF)))
FFFF<-dfFFFF$`NRMSE %`

obsGGGG<-c(data$T10.AP)
simGGGG<-c(five_four_imp$T10.AP)
dfGGGG<-as.data.frame(t(gof(sim=simGGGG, obs=obsGGGG)))
GGGG<-dfGGGG$`NRMSE %`

obsHHHH<-c(data$T10.TR)
simHHHH<-c(five_four_imp$T10.TR)
dfHHHH<-as.data.frame(t(gof(sim=simHHHH, obs=obsHHHH)))
HHHH<-dfHHHH$`NRMSE %`

obsIIII<-c(data$L1.AP)
simIIII<-c(five_four_imp$L1.AP)
dfIIII<-as.data.frame(t(gof(sim=simIIII, obs=obsIIII)))
IIII<-dfIIII$`NRMSE %`

obsJJJJ<-c(data$L1.TR)
simJJJJ<-c(five_four_imp$L1.TR)
dfJJJJ<-as.data.frame(t(gof(sim=simJJJJ, obs=obsJJJJ)))
JJJJ<-dfJJJJ$`NRMSE %`

obsKKKK<-c(data$L3.AP)
simKKKK<-c(five_four_imp$L3.AP)
dfKKKK<-as.data.frame(t(gof(sim=simKKKK, obs=obsKKKK)))
KKKK<-dfKKKK$`NRMSE %`

obsLLLL<-c(data$L3.TR)
simLLLL<-c(five_four_imp$L3.TR)
dfLLLL<-as.data.frame(t(gof(sim=simLLLL, obs=obsLLLL)))
LLLL<-dfLLLL$`NRMSE %`
```

#five_five_imp
```{r}
obsAAAAA<-c(data$FL.Left)
simAAAAA<-c(five_five_imp$FL.Left)
dfAAAAA<-as.data.frame(t(gof(sim=simAAAAA, obs=obsAAAAA)))
AAAAA<-dfAAAAA$`NRMSE %`

obsBBBBB<-c(data$FL.Right)
simBBBBB<-c(five_five_imp$FL.Right)
dfBBBBB<-as.data.frame(t(gof(sim=simBBBBB, obs=obsBBBBB)))
BBBBB<-dfBBBBB$`NRMSE %`

obsCCCCC<-c(data$T1.AP)
simCCCCC<-c(five_five_imp$T1.AP)
dfCCCCC<-as.data.frame(t(gof(sim=simCCCCC, obs=obsCCCCC)))
CCCCC<-dfCCCCC$`NRMSE %`

obsDDDDD<-c(data$T1.TR)
simDDDDD<-c(five_five_imp$T1.TR)
dfDDDDD<-as.data.frame(t(gof(sim=simDDDDD, obs=obsDDDDD)))
DDDDD<-dfDDDDD$`NRMSE %`

obsEEEEE<-c(data$T5.AP)
simEEEEE<-c(five_five_imp$T5.AP)
dfEEEEE<-as.data.frame(t(gof(sim=simEEEEE, obs=obsEEEEE)))
EEEEE<-dfEEEEE$`NRMSE %`

obsFFFFF<-c(data$T5.TR)
simFFFFF<-c(five_five_imp$T5.TR)
dfFFFFF<-as.data.frame(t(gof(sim=simFFFFF, obs=obsFFFFF)))
FFFFF<-dfFFFFF$`NRMSE %`

obsGGGGG<-c(data$T10.AP)
simGGGGG<-c(five_five_imp$T10.AP)
dfGGGGG<-as.data.frame(t(gof(sim=simGGGGG, obs=obsGGGGG)))
GGGGG<-dfGGGGG$`NRMSE %`

obsHHHHH<-c(data$T10.TR)
simHHHHH<-c(five_five_imp$T10.TR)
dfHHHHH<-as.data.frame(t(gof(sim=simHHHHH, obs=obsHHHHH)))
HHHHH<-dfHHHHH$`NRMSE %`

obsIIIII<-c(data$L1.AP)
simIIIII<-c(five_five_imp$L1.AP)
dfIIIII<-as.data.frame(t(gof(sim=simIIIII, obs=obsIIIII)))
IIIII<-dfIIIII$`NRMSE %`

obsJJJJJ<-c(data$L1.TR)
simJJJJJ<-c(five_five_imp$L1.TR)
dfJJJJJ<-as.data.frame(t(gof(sim=simJJJJJ, obs=obsJJJJJ)))
JJJJJ<-dfJJJJJ$`NRMSE %`

obsKKKKK<-c(data$L3.AP)
simKKKKK<-c(five_five_imp$L3.AP)
dfKKKKK<-as.data.frame(t(gof(sim=simKKKKK, obs=obsKKKKK)))
KKKKK<-dfKKKKK$`NRMSE %`

obsLLLLL<-c(data$L3.TR)
simLLLLL<-c(five_five_imp$L3.TR)
dfLLLLL<-as.data.frame(t(gof(sim=simLLLLL, obs=obsLLLLL)))
LLLLL<-dfLLLLL$`NRMSE %`
```

Put each NRMSE into a matrix to create a usable dataframe that can be exported to Excel
```{r}
aa<-matrix(c(A, B, C, D, E, F, G, H, I, J, K, L), 1, 12)

ab<-matrix(c(AA, BB, CC, DD, EE, FF, GG, HH, II, JJ, KK, LL), 1, 12)

ac<-matrix(c(AAA, BBB, CCC, DDD, EEE, FFF, GGG, HH, III, JJJ, KKK, LLL), 1, 12)

ad<-matrix(c(AAAA, BBBB, CCCC, DDDD, EEEE, FFFF, GGGG, HHHH, IIII, JJJJ, KKKK, LLLL), 1, 12)

ae<-matrix(c(AAAAA, BBBBB, CCCCC, DDDDD, EEEEE, FFFFF, GGGGG, HHHHH, IIIII, JJJJJ, KKKKK, LLLLL), 1, 12)

df.cont.rf<-data.frame(rbind(aa, ab, ac, ad, ae))
colnames(df.cont.rf)<-c("FL.Left", "FL.Right", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
rownames(df.cont.rf)<-c("five_one_imp", "five_two_imp", "five_three_imp", "five_four_imp", "five_five_imp")
write.csv(df.cont.rf, file="nrmse.continuous.rf.practice.csv")
```