#####Simulating missing values in continuous and ordinal datasets####

#This code creates all the ordinal and continuous datasets with missing percentages of data
```{r}
rm(list=ls())
library(knitr)
library(imputeR)

setwd("C:/Users/Amanda Wissler/Documents/Spring 2022/Manuscripts/MIssing data II/R code/GitHub")
data.ordinal<-read.csv("Practice.Ordinal.Dataset.csv", header=T)
```


#Simulate 5% missingness into ordinal dataset using ImputeR "SimIm" function
```{r}
set.seed(1)
ord.five.1<-SimIm(data.ordinal, p=0.05)
ord.five.2<-SimIm(data.ordinal, p=0.05)
ord.five.3<-SimIm(data.ordinal, p=0.05)
ord.five.4<-SimIm(data.ordinal, p=0.05)
ord.five.5<-SimIm(data.ordinal, p=0.05)
```


#SimIM doesn't keep the row names so we have to add them back and export as .csv
#For 5% missingness
```{r}
colnames(ord.five.1)<-c("PH", "CO", "PD", "LEH", "periostosis")
write.csv(ord.five.1, file="ord.five.1.practice.csv")

colnames(ord.five.2)<-c("PH", "CO", "PD", "LEH", "periostosis")
write.csv(ord.five.2, file="ord.five.2.practice.csv")

colnames(ord.five.3)<-c("PH", "CO", "PD", "LEH", "periostosis")
write.csv(ord.five.3, file="ord.five.3.practice.csv")

colnames(ord.five.4)<-c("PH", "CO", "PD", "LEH", "periostosis")
write.csv(ord.five.4, file="ord.five.4.practice.csv")

colnames(ord.five.5)<-c("PH", "CO", "PD", "LEH", "periostosis")
write.csv(ord.five.5, file="ord.five.5.practice.csv")
```


#####Continous Data####

```{r}
data.continuous<-read.csv("Practice.Continuous.Dataset.csv", header=T)
```

#Simulate 5% missingness into ordinal dataset using ImputeR "SimIm" function
```{r}
set.seed(1)
cont.five.1<-SimIm(data.continuous, p=0.05)
cont.five.2<-SimIm(data.continuous, p=0.05)
cont.five.3<-SimIm(data.continuous, p=0.05)
cont.five.4<-SimIm(data.continuous, p=0.05)
cont.five.5<-SimIm(data.continuous, p=0.05)
```

```{r}
colnames(cont.five.1)<-c("FL.L", "FL.R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.1, file="cont.five.1.practice.csv")

colnames(cont.five.2)<-c("FL.L", "FL.R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.2, file="cont.five.2.practice.csv")

colnames(cont.five.3)<-c("FL.L", "FL.R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.3, file="cont.five.3.practice.csv")

colnames(cont.five.4)<-c("FL.L", "FL.R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.4, file="cont.five.4.practice.csv")

colnames(cont.five.5)<-c("FL.L", "FL.R", "T1.AP", "T1.TR", "T5.AP", "T5.TR", "T10.AP", "T10.TR", "L1.AP", "L1.TR", "L3.AP", "L3.TR")
write.csv(cont.five.5, file="cont.five.5.practice.csv")
```